## Access specific elements
The `eml_get` function is a powerful tool for exploring EML (more on that [here](https://cran.rstudio.com/web/packages/EML/vignettes/parsing-EML.html)). It takes any chunk of `EML` and returns _all instances_ of the element you specify. _Note:_ you'll have to specify the element of interest exactly, according to the spelling/capitalization conventions used in EML. Here are some examples:

```{r "creator", eval = FALSE}
eml <- EML::read_eml(system.file("example-eml.xml", package = "arcticdatautils"))
EML::eml_get(eml, "creator")
```
```
[[1]]
An object of class "ListOfcreator"
[[1]]
<creator system="uuid">
  <individualName>
    <givenName>Bryce</givenName>
    <surName>Mecum</surName>
  </individualName>
  <organizationName>National Center for Ecological Analysis and Synthesis</organizationName>
</creator>
```


```{r "boundingCoords", eval = FALSE}
EML::eml_get(eml, "boundingCoordinates")
```
```
<boundingCoordinates>
  <westBoundingCoordinate>-135</westBoundingCoordinate>
  <eastBoundingCoordinate>-134</eastBoundingCoordinate>
  <northBoundingCoordinate>59</northBoundingCoordinate>
  <southBoundingCoordinate>57</southBoundingCoordinate>
</boundingCoordinates>
```


```{r "url", eval = FALSE}
EML::eml_get(eml, "url")
```
```
[1] "ecogrid://knb/urn:uuid:89bec5d0-26db-48ac-ae54-e1b4c999c456"
```

You can also use the `which_in_eml` function from the `datamgmt` package to get indices within an `EML` list. Here are some examples:

```{r "which_in_eml", eval = FALSE}
# Question: Which creators have a surName "Smith"?
n <- which_in_eml(eml@dataset@creator, "surName", "Smith")
# Answer: eml@dataset@creator[n]

# Question: Which dataTables have an entityName that begins with "2016"
n <- which_in_eml(eml@dataset@dataTable, "entityName", function(x) {grepl("^2016", x)})
# Answer: eml@dataset@dataTable[n]

# Question: Which attributes in dataTable[[1]] have a numberType "natural"?
n <- which_in_eml(eml@dataset@dataTable[[1]]@attributeList@attribute, "numberType", "natural")
# Answer: eml@dataset@dataTable[[1]]@attributeList@attribute[n]

#' # Question: Which dataTables have at least one attribute with a numberType "natural"?
n <- which_in_eml(eml@dataset@dataTable, "numberType", function(x) {"natural" %in% x})
# Answer: eml@dataset@dataTable[n]
```
