## Access specific elements

The `eml_get()` function is a powerful tool for exploring EML (more on that [here](https://ropensci.github.io/EML/)). It takes any chunk of EML and returns _all instances_ of the element you specify. _Note:_ you'll have to specify the element of interest exactly, according to the spelling/capitalization conventions used in EML. Here are some examples:

```{r "creator", eval = FALSE}
doc <- read_eml(system.file("example-eml.xml", package = "arcticdatautils"))
eml_get(doc, "creator")
```
```
individualName:
  givenName: Bryce
  surName: Mecum
organizationName: National Center for Ecological Analysis and Synthesis
```

```{r "boundingCoords", eval = FALSE}
eml_get(doc, "boundingCoordinates")
```
```
eastBoundingCoordinate: '-134'
northBoundingCoordinate: '59'
southBoundingCoordinate: '57'
westBoundingCoordinate: '-135'
```

```{r "url", eval = FALSE}
eml_get(doc, "url")
```
```
'':
  function: download
  url: ecogrid://knb/urn:uuid:89bec5d0-26db-48ac-ae54-e1b4c999c456
'': ecogrid://knb/urn:uuid:89bec5d0-26db-48ac-ae54-e1b4c999c456
```

`eml_get_simple()` is a simplified alternative to `eml_get()` that produces a list of the desired EML element.

```{r "eml_get_simple", eval = FALSE}
eml_get_simple(doc$dataset$otherEntity, "entityName")
```

To find an eml element you can use either a combination of `which_in_eml`from the `datamgmt` package or `eml_get_simple` and `which` to find the index in an EML list. Use which ever workflow you see 
fit.

**An example question you may have:** *Which creators have a surName "Mecum"?*

Example using `which_in_eml`:

```{r "which_in_eml", eval = FALSE}
n <- which_in_eml(doc$dataset$creator, "surName", "Mecum")
# Answer: doc$dataset$creator[[n]]
```

Example using `eml_get_simple` and `which`:

```{r "getting index using eml_get_simple", eval = FALSE}
ent_names <- eml_get_simple(doc$dataset$creator, "surName")
i <- which(ent_names == "Mecum")
# Answer: doc$dataset$creator[[i]]
```
