## Access specific elements
The `eml_get` function is a powerful tool for exploring EML (more on that [here](https://cran.rstudio.com/web/packages/EML/vignettes/parsing-EML.html)). It takes any chunk of `eml` and returns _all instances_ of the element you specify. _Note:_ you'll have to specify the element of interest exactly, according to the spelling/capitalization conventions used in EML. Here are some examples:

```{r echo = FALSE, message = FALSE, warning = FALSE}
library(arcticdatautils) #load to grab package
```

```{r "creator"}
eml <- EML::read_eml(system.file("example-eml.xml", package = "arcticdatautils"))
EML::eml_get(eml, "creator")
```

```{r "boundingCoords"}
EML::eml_get(eml, "boundingCoordinates")
```

```{r "url"}
EML::eml_get(eml, "url")
```

You can also use the `which_in_eml` function from the `datamgmt` package to get indices within an `eml` list. Here are some examples:

```{r "which_in_eml", eval = FALSE}
# Question: Which creators have a surName "Smith"?
n <- which_in_eml(eml@dataset@creator, "surName", "Smith")
# Answer: eml@dataset@creator[n]

# Question: Which dataTables have an entityName that begins with "2016"
n <- which_in_eml(eml@dataset@dataTable, "entityName", function(x) {grepl("^2016", x)})
# Answer: eml@dataset@dataTable[n]

# Question: Which attributes in dataTable[[1]] have a numberType "natural"?
n <- which_in_eml(eml@dataset@dataTable[[1]]@attributeList@attribute, "numberType", "natural")
# Answer: eml@dataset@dataTable[[1]]@attributeList@attribute[n]

#' # Question: Which dataTables have at least one attribute with a numberType "natural"?
n <- which_in_eml(eml@dataset@dataTable, "numberType", function(x) {"natural" %in% x})
# Answer: eml@dataset@dataTable[n]
```
