## datapack Background
*adapted from the dataone and datapack vingettes*

`datapack` is written differently than most R packages you may have encountered in the past. This is because it uses the [S4](https://adv-r.hadley.nz/s4.html) system instead.

```{r , eval = F}
library(dataone)
library(datapack)
library(uuid)
```

### Data packages

Data packages are a class that has slots for `relations` (provenance), `objects`(the metadata and data file(s)) and `systemMetadata`.

### Navigating data packages

#### Nodes
Using this example on arcticdata.io
```{r, eval = F}
d1c_test <- dataone::D1Client("STAGING", "urn:node:mnTestARCTIC")
```

To use the member node information, use the `mn` slot
```{r, eval = F}
d1c_test@mn
```

```{block, type = "note"}
To access the various slots using objects created by datapack and dataone (e.g. `getSystemMetadata`) requires the `@` which is different from what you might have seen in the past. This is because these use the [S4](https://adv-r.hadley.nz/s4.html) system.
```

Get an existing package from the Arctic Data Center
```{r, eval=F}
dp <- dataone::getDataPackage(d1c, "resource_map_urn:uuid:1f9eee7e-2d03-43c4-ad7f-f300e013ab28")
```


#### Data
Check out the `objects` slot
```{r, eval=F}
dp@objects
```

Get the number for data and metadata files associated with this data package:
```{r, eval=F}
length(dp@objects)
```

#### Provenance
View the provenance as a dataTable. We will get into detail in the Building provenance chapter.
```{r, eval=F}
dp@relations$relations
```

##### Get identifiers
You can search by any of the `sysmeta` slots such as `fileName` and `formatId` and get the corresponding identifier(s):
```{r, eval = F}
metadataId <- selectMember(dp, name="sysmeta@ADD THE NAME OF THE SLOT", value="PATTERN TO SEARCH BY")
```

For example:
```{r, eval = F}
selectMember(dp, name="sysmeta@formatId", value="image/tiff")
selectMember(dp, name="sysmeta@fileName", value="filename.csv")
```

### Exercise 2a {.exercise}

Select a dataset from the catalog on arcticdata.io and checkout the number of files and provencance relationships in the dataset.

