## Datapack Background
*adapted from the dataone and datapack vingettes*

```{r , eval = F}
library(dataone)
library(datapack)
library(uuid)
```

### Data packages

Data packages are a class that has slots for `relations` (provenance), `objects`(the metadata and data file(s)) and `systemMetadata`.

### Navigating data packages

#### Nodes
Using this example on arcticdata.io
```{r}
d1c <- dataone::D1Client("PROD", "urn:node:ARCTIC")
```

To use the member node information, use the `mn` slot
```{r, eval = F}
d1c@mn
```

```{block, type = "note"}
To access the various slots using objects created by datapack and dataone (e.g. `getSystemMetadata`) requires the `@` which is different from what you might have seen in the past. This is because these use the [S4](https://adv-r.hadley.nz/s4.html) system.
```

Get an existing package from the Arctic Data Center
```{r}
dp <- dataone::getDataPackage(d1c, "resource_map_urn:uuid:1f9eee7e-2d03-43c4-ad7f-f300e013ab28")
```


#### Data
Check out the `objects` slot
```{r, eval=F}
dp@objects
```

Get the number for data and metadata files associated with this data package:
```{r}
length(dp@objects)
```

Grab only the data pids
```{r}
names(dp@objects)
```

Get the file name:
```{r}
dp@objects$`urn:uuid:e6390181-85e9-46a2-b2ba-e352ece51cc6`@sysmeta@fileName
```

#### Provenance
View the provenance as a dataTable. 
```{r}
dp@relations$relations
```

##### Get identifiers
You can search by any of the `sysmeta` slots such as `fileName` and `formatId` and get the corresponding identifier(s):
```{r, eval = F}
metadataId <- selectMember(dp, name="sysmeta@ADD THE NAME OF THE SLOT", value="PATTERN TO SEARCH BY")
```

For example:
```{r, eval = F}
selectMember(dp, name="sysmeta@formatId", value="image/tiff")
```

### Exercise
```
Select a dataset from the catalog on arcticdata.io and checkout the number of files and provencance relationships in the dataset.
```
