## Datapack Background
*adapted from the dataone and datapack vingettes*

```{r , eval = F}
library(dataone)
library(datapack)
library(uuid)
```

### Data packages

Data packages are a class that has slots for `relations` (provenance), `objects`(the metadata and data file(s)) and `systemMetadata`.

### Navigating data packages

Using this example on arcticdata.io
```{r}
d1c <- dataone::D1Client("PROD", "urn:node:ARCTIC")

dp <- dataone::getDataPackage(d1c, "resource_map_urn:uuid:1f9eee7e-2d03-43c4-ad7f-f300e013ab28")
```

Check out the `objects` slot
```{r, eval=F}
dp@objects
```

Get the number for data and metadata files associated with this data package:
```{r}
length(dp@objects)
```


Get the file name:
```{r}
dp@objects$`urn:uuid:e6390181-85e9-46a2-b2ba-e352ece51cc6`@sysmeta@fileName
```


The provenance relations is a dataTable. 

```{r}
dp@relations$relations
```

### Exercise
```
Select a dataset from the catalog on arcticdata.io and checkout the number of files and provencance relationships in the dataset.
```
