## Update packages with datapack

Once you have updated the data objects and saved the metadata to a file, we can update the metadata and add the new `pid` to the resource map using `datapack::updateDataObject()`.

```{block, type = "note"}
This part of the training assumes that you have an EML file created from earlier parts of the training
```


```{block, type = "warning"}
You must use these R packages for data packages that have provenance or folder hierarchy (`arcticdatatutils` does not support those features)
```

### Get the package

Setting the node is done slightly differently:
```{r, eval = F}
d1c <- dataone::D1Client("STAGING", "urn:node:mnTestARCTIC")
```

Get a pre-existing package:
```{r, eval = F}
packageId <- "the resource map"

pkg <- getDataPackage(d1c, identifier=packageId, lazyLoad=TRUE, quiet=FALSE)
```

### Update the metadata

Get the metadata identifier
```{r, eval = F}
metadataId <- selectMember(pkg, name="sysmeta@formatId", value="https://eml.ecoinformatics.org/eml-2.2.0")
```

Now we can update your data package to include the new metadata file
```{r, eval = F}
eml_path <- "path/to/your/saved/eml.xml"
write_eml(doc, eml_path)

pkg <- replaceMember(pkg, metadataId, replacement=eml_path)
```

### Modify the data files

remove zip files
```{r, eval = F}
zipId <- selectMember(dp, name="sysmeta@formatId", value="application/vnd.shp+zip")
removeMember(dp, zipId, removeRelationships = T)
```

add an existing data object

```{r, eval = F}
dataObj <- getDataObject(d1c, id="urn:uuid: here", lazyLoad=T, limit="1TB")
dp <- addMember(dp, dataObj, mo=metadataId)
```

```{block, type = "note"}
If you want to change the formatId please use `updateSystemMetadata`
```

### Publish update

Publishing with a UUID
```{r, eval = FALSE}
newPackageId <- uploadDataPackage(d1c, pkg, public=FALSE, quiet=FALSE)
```
If a package is ready to be public, you can change the `public` argument in the `uploadDataPackage()` call to `TRUE`.


#### Using a Digital Object Identifier (DOI)

**This should only be done after the package is finalized and has been thoroughly reviewed!**

A Digital Object Identifier (DOI) may be assigned to the metadata **DataObject**, using the `generateIdentifier`:
```{r, eval=FALSE}
doi <- dataone::generateIdentifier(d1c@mn, "DOI")
pkg <- replaceMember(pkg, metadataId, replacement=eml_path, newId = doi)

newPackageId <- uploadDataPackage(d1c, pkg, public=TRUE, quiet=FALSE)
``` 



Refresh the landing page at test.arcticdata.io/#view/... for this package and then follow the "newer version" link to view the latest.
