## Email templates

Please think critically when using these canned replies rather than just blindly sending them. Typically, content should be adjusted/ customized for each response to be as relevant, complete, and precise as possible.  

In your first few months, please run email drafts by the #datateam Slack and get approval before sending.

Remember to consult the <a href = 'https://arcticdata.io/submit/' target='_blank'>submission guidelines</a> for details of what is expected.  

Quick reference:
- [Initial email template](https://nceas.github.io/datateam-training/reference/email-templates.html#initial-email-template)
- [Final email templates](https://nceas.github.io/datateam-training/reference/email-templates.html#final-email-templates)
- [Additional email template](https://nceas.github.io/datateam-training/reference/email-templates.html#additional-email-templates)

```{r, echo = FALSE}
chapter <- "email_templates/"
sections <- dir(path = chapter, pattern = ".Rmd$")
children <- paste0(chapter, sections)
```

```{r, child = children}
```
