## Query Solr through R

Though it's possible to [query Solr directly through its HTTP API](#query-solr), we typically run our queries through R, for two main reasons: 

1. The result is returned in a more useful way to R without extra work on your part
2. We can more easily pass our authentication token with the query

Why does #2 matter?
Well by default, all of those URLs above only returned publicly-readable Solr documents.
If a private document matched any of those queries, Solr doesn't give you any idea and acts like the non-public-readable documents don't exist. So we must pass an authentication token to access non-public-readable content. This bit is crucial for working with the ADC, so you'll very often want to use R instead of visiting those URLs in a web browser.

```{r}
cn <- dataone::CNode("PROD")
mn <- dataone::getMNode(cn, "urn:node:ARCTIC")
# Set your token if you need/want!

#string your parameters together like this: dataone::query(mn, "q=title:*soil*&fl=title&rows=10")
#or alternatively, list them out:
dataone::query(mn, list(q="title:*soil*",
                        fl="title",
                        rows="10"))
```

By default, `query` returns the result as a `list`, but a `data.frame` can be a more useful way to work with the result. To get a `data.frame` instead, just set the `as` argument to 'data.frame' to get a `data.frame`:

```{r eval = TRUE}
dataone::query(mn, list(q="title:*soil*",
                        fl="title",
                        rows="10"),
               as = "data.frame")
```
