## MOSAiC

Look out for datasets that are part of the MOSAiC expedition from 2019 -2020. There are a couple of special steps for datasets from this project.

**When working on MOSAiC datasets:**

1. Find out the `EventId` from the researcher to annotate (`Campaign` can be derived from the `eventLabel`). Ask for it in your email:

> We would like to ask for the event label associated with this dataset (see https://www.pangaea.de/expeditions/events/PS122%2F4).

Often times researchers do not have a full list of event labels, but instrument names are provided in the dataset metadata. In these cases, try to find the correct event labels by searching through the event lists and finding matching instrument names and dates. Each MOSAiC [campaign](https://www.pangaea.de/expeditions/byproject/MOSAiC) has its own event list. [Here](https://www.pangaea.de/expeditions/events/PS122%2F1) is an example of an event list for the first cruise by the Polarstern research vessel.

2. Find the appropriate dataset and attribute level annotations

- There are functions in `arcticdatautils` to help with annotating: `mosaic_annotate_dataset` and `mosaic_annotate_attribute`
- The custom ontology for the datasets are currently in the [sem-prov-ontologies](https://github.com/DataONEorg/sem-prov-ontologies/blob/main/MOSAiC/MOSAiC.owl) repository but you won't need to use it directly if the function works.
- Use `EML::shiny_attributes` only when no annotations have been added. The function does not work well with multiple annotations
- Please continue to annotate the measurement types using `containst measurements of type` for all other attributes

3. The [portal](https://search.dataone.org/portals/mosaic/Data) is on DataONE. Make sure the dataset(s) show up in the portal after you add the annotations.

**Here are two fully annotated datasets for reference:**

1. [Simple example](https://doi.org/10.18739/A27S7HT3B)
2. [Example with MOSAiC and ECSO annotations](https://doi.org/10.18739/A2M03XZ32)
3. [Example with non-polarstern vessels](https://arcticdata.io/catalog/view/urn%3Auuid%3A679b719b-2feb-4b61-a975-282149995b51)

The following shows how to add the annotations using `arcticdatautils` and manually in the case the functions fail to work:

### Dataset Level Annotations

There are 5 main campaigns in the MOSAiC expedition. The main campaigns follow the pattern `PS122/#`. The full campaign list is easiest to view on the [PANGAEA website](https://www.pangaea.de/expeditions/byproject/MOSAiC). The first two letters of each campaign name correspond with the ship or station name (ex: PS = Polarstern).

**arcticdatautils**
```{r, eval = F}
doc$dataset$id <- "your id here"
doc$dataset$annotation <- NULL #make sure it is empty

doc$dataset$annotation <- mosaic_annotate_dataset(c("PS122/1", "PS122/2"))
```

**Manual**

Majority of the annotations will be the same across all of the datasets. Pay attention to what needs to be changed for the `hasBasis` and `isPartOfCampaign` valueURIs.

More than one `Campaign` and `Basis` might be needed in rare cases.

```{r, eval = F}
doc$dataset$id <- "your id here"
doc$dataset$annotation <- NULL #make sure it is empty here

doc$dataset$annotation <- list(
  #Basis
  list(
    propertyURI = list(label = "hasBasis",
                       propertyURI = "https://purl.dataone.org/odo/MOSAIC_00000034"),
    valueURI = list(label = "Polarstern", # this depends on your event ID, most of them should be Polarstern
                    valueURI = "https://purl.dataone.org/odo/MOSAIC_00000030")
  ),
  #Project
  list(
    propertyURI = list(label = "hasProjectLabel",
                       propertyURI = "https://purl.dataone.org/odo/MOSAIC_00000025"),
    valueURI = list(label = "MOSAiC20192020",
                    valueURI = "https://purl.dataone.org/odo/MOSAIC_00000023")
  ),
  #Campaign
  list(
    propertyURI = list(label = "isPartOfCampaign",
                       propertyURI = "https://purl.dataone.org/odo/MOSAIC_00000032"),
    valueURI = list(label = "PS122/2", #*** this changes depending on the campaign
                    valueURI = "https://purl.dataone.org/odo/MOSAIC_00000018")
  ) #*** this changes depending on the campaign
)
```

#### Attribute Level Annotations

Apply these to the attribute level of the dataset. Event IDs should have already be identified earlier on in the dataset review. Check the ticket overview for details.

**arcticdatautils**

```{r, eval = F}
doc$dataset$dataTable[[1]]$attributeList$attribute[[1]]$id <- "some id here"
doc$dataset$dataTable[[1]]$attributeList$attribute[[1]]$annotation <- mosaic_annotate_attribute("PS122/2_14-270")
```

**Manual**
```{r, eval = F}
event_annotation <- list(#Event Label
  list(
    propertyURI = list(label = "wasGeneratedBy",
                       propertyURI = "http://www.w3.org/ns/prov#wasGeneratedBy"),
    valueURI = list(label = "PS122/2_14-270",
                    valueURI = "https://purl.dataone.org/odo/MOSAIC_00004550")
  ),
  #Method/Device - Use the long name!
  list(
    propertyURI = list(label = "deployedSystem",
                       propertyURI = "https://purl.dataone.org/odo/MOSAIC_00002201"),
    valueURI = list(label = "Ultra-Wideband Software-defined Microwave Radiometer (0.5-2GHZ)",
                    valueURI = "https://purl.dataone.org/odo/MOSAIC_00001163")
  ))

doc$dataset$dataTable$attributeList$attribute[[1]]$id <- "eventId"
doc$dataset$dataTable$attributeList$attribute[[1]]$annotation <-
  event_annotate
```


**Adding annotations**

If there are already annotations applied (ie. using ECSO), the MOSAiC annotations can be added as so:

1. get the index of all of the attributes we want to add this annotation
```{r, eval = F}
n <- which(stringr::str_detect(eml_get_simple(doc$dataset$dataTable$attributeList, "attributeName"),"Brightness"))
```

2. loop through and add the annotation(s)
```{r, eval = F}
for(i in n) {
  doc$dataset$dataTable$attributeList$attribute[[i]]$annotation <-
    append(
      list(
        doc$dataset$dataTable$attributeList$attribute[[i]]$annotation
      ),
      event_annotation
    )
}
```

### Portal updates

The filters are based on the MOSAiC ontology. The `Campaign` and `Basis` filters should remain relatively the same. However there are over 500 Method and Devices. So the decision was made to only show the ones we have annotated.

We can query for all of them and output them formatted as a choice:

```{r eval = F}
mosaic_portal_filter("Method/Device")
```

Then update the portal document using the steps outlines in the [advanced data portal customizations](https://nceas.github.io/datateam-training/reference/data-portals-1.html)
