## MOSAiC

Look out for datasets that are part of the MOSAiC expedition from 2019 -2020. There are a couple of special steps for datasets from this project.

## Data Portal

The [portal](https://search.dataone.org/portals/mosaic/Data) is on DataONE. Make sure the dataset(s) shows up in the portal after you add the annotations.

### Custom Ontology

There is a custom ontology for the datasets (the ontology will be available publicly shortly - for now ask on #datateam for access to the annotations you need). 

#### Dataset Level Annotations

Majority of the annotations will be the same across all of the datasets. Pay attention to what needs to be changed for the `hasBasis` and `isPartOfCampaign` valueURIs.

More than one `Campaign` and `Basis` might be needed in rare cases.

```{r, eval = F}
doc$dataset$id <- "your id here"
doc$dataset$annotation <- NULL #make sure it is empty here

doc$dataset$annotation <- list(
  #Basis
  list(propertyURI = list(label = "hasBasis", 
                          propertyURI = "http://purl.dataone.org/odo/MOSAiC_00000034"), 
       valueURI = list(label = "Polarstern", # this depends on your event ID, most of them should be Polarstern
                       valueURI = "http://purl.dataone.org/odo/MOSAiC_00000030")),
  #Project
  list(propertyURI = list(label = "hasProjectLabel", 
                          propertyURI = "http://purl.dataone.org/odo/MOSAiC_00000025"), 
       valueURI = list(label = "MOSAiC20192020", 
                       valueURI = "http://purl.dataone.org/odo/MOSAiC_00000023")),
  #Campaign 
  list(propertyURI = list(label = "isPartOfCampaign", 
                          propertyURI = "http://purl.dataone.org/odo/MOSAiC_00000032"), 
       valueURI = list(label = "PS122/2", #*** this changes depending on the leg
                       valueURI = "http://purl.dataone.org/odo/MOSAiC_00000018")) #*** this changes depending on the leg
)
```

There are 5 legs in the MOSAiC expedition. They all follow the pattern `PS122/#`. Replace the following for the corresponding leg.
```{r}
list(propertyURI = list(label = "isPartOfCampaign", 
                        propertyURI = "http://purl.dataone.org/odo/MOSAiC_00000032"), 
     valueURI = list(label = "leg label here", 
                     valueURI = "leg uri here"))
```

#### Entity Level Annotations

Apply these to the attribute level of the dataset. Event IDs should have already be identified earlier on in the dataset review. Check the ticket overview for details.

```{r, eval = F}
event_annotate <- list(
  #Event Label
  list(propertyURI = list(label = "wasGeneratedBy", 
                          propertyURI = "http://www.w3.org/ns/prov#wasGeneratedBy"), 
       valueURI = list(label = "PS122/2_14-270", 
                       valueURI = "http://purl.dataone.org/odo/MOSAiC_00004550")),
  #Method/Device - Use the long name!
  list(propertyURI = list(label = "deployedSystem", 
                          propertyURI = "http://purl.dataone.org/odo/MOSAiC_00002201"), 
       valueURI = list(label = "Ultra-Wideband Software-defined Microwave Radiometer (0.5-2GHZ)", 
                       valueURI = "http://purl.dataone.org/odo/MOSAiC_00001163"))
  
)

doc$dataset$dataTable$attributeList$attribute[[i]]$annotation <- event_annotate
```

If there are already annotations applied using ECSO, the MOSAiC annotations can be added as so:

1. get the index of all of the attributes we want to add this annotation
```{r, eval = F}
n <- which(stringr::str_detect(eml_get_simple(doc$dataset$dataTable$attributeList, "attributeName"),"Brightness"))
```

2. loop through and add the annotation(s)
```{r, eval = F}
for(i in n){
  doc$dataset$dataTable$attributeList$attribute[[i]]$annotation <- append(list(doc$dataset$dataTable$attributeList$attribute[[i]]$annotation),
                                                                          event_annotate)
}
```
