# Exploring EML

We use the Ecological Metadata Language (EML) to store structured metadata for all datasets submitted to the Arctic Data Center. EML is written in XML (extensible markup language) and functions for building and editing EML are in the <a href = 'https://github.com/ropensci/EML' target='_blank'>EML R package</a>.

Currently the Arctic Data Center website supports editing EML version 2.2.0. There are still some metadata in 2.1.1 that will be converted eventually. 

For additional background on EML and principles for metadata creation, check out <a href = 'data/eml-principles.pdf' target='_blank'>this paper</a>.

If you aren't too familiar with lists and how to navigate them yet take a look at the relevant sections in the <a href = 'https://stat545.com/r-objects.html#lists-hold-just-about-anything' target='_blank'>Stat 545 class.</a> 

```{r, child = '../workflows/explore_eml/navigate_through_eml.Rmd'}
```

```{r, child = '../workflows/explore_eml/understand_eml_schema.Rmd'}
```

### Check your understanding {.exercise}
* Find `otherEntity` within the EML schema. Which elements are required? Can `otherEntity` be a series object?

<details>
<summary>Answer</summary>
<br>
`otherEntity` requires `entityType` and `entityName` children, or alternatively will accept only `references`. It is a series object, so there can be multiple `otherEntities`. Along with `otherEntity` and `creator`, `dataTable` and `attribute` can also be series objects.
</details>

```{r, child = '../workflows/explore_eml/access_specific_elements.Rmd'}
```
