# Editing EML

This chapter is a practical tutorial for using R to read, edit, write, and validate EML documents. Much of the information here can also be found in the vignettes for the R packages used in this section (e.g. the <a href = 'https://github.com/ropensci/EML/blob/master/vignettes/creating-EML.Rmd' target='_blank'>EML package</a>).

```{block, type = "note"}
This chapter will be longest of all the sections! This is a reminder to take frequent breaks when completing this section.
```

```{r, child = '../workflows/edit_data_packages/get_package_and_eml.Rmd'}
```

```{r, child = '../workflows/edit_eml/edit_an_eml_element.Rmd'}
```

## FAIR data practices

To make sure our EML has a publisher and entity system associated

Add the following lines to all of your data processing scripts.
```{r, eval= FALSE}
  doc <- eml_add_publisher(doc)
  doc <- eml_add_entity_system(doc)
```

```{r, child = '../workflows/edit_eml/edit_attributelists.Rmd'}
```

```{r, child = '../workflows/edit_eml/set_physical.Rmd'}
```

```{r, child = '../workflows/edit_eml/edit_datatables.Rmd'}
```

```{r, child = '../workflows/edit_eml/edit_otherentities.Rmd'}
```

## Exercise 3a {.exercise}

* Make sure your package from [before](#exercise-2) is loaded into R.
* Replace the existing `dataTable` with a new `dataTable` object with an `attributelist` and `physical` section you write in R using the above commands.
* We will continue using the objects created and updated in this exercise in 3b

```{r, child = '../workflows/edit_eml/edit_spatialdata.Rmd'}
```

```{r, child = '../workflows/edit_eml/set_coverages.Rmd'}
```

```{r, child = '../workflows/edit_eml/set_methods.Rmd'}
```

```{r, child = '../workflows/edit_eml/set_parties.Rmd'}
```

## Validate EML and update package

To make sure that your edited EML is valid against the EML schema, run `eml_validate()` on your EML. Fix any errors that you see.

```{r, eval = F}
eml_validate(doc)
```

You should see something like if everything passes:
>[1] TRUE
>attr(,"errors")
>character(0)

Then save your EML to a path of your choice or a temp file. You will later pass this path as an argument to update the package.

```{r, eval = F}
eml_path <- "path/to/save/eml.xml"
write_eml(doc, eml_path)
```



To update a package with the newly edited EML, use `arcticdatautils::publish_update()`. This function has an argument for adding data `PID`s (or otherwise including existing data `PID`s) to make sure that they stay with the package. This function allows you to make metadata edits, as well as add or remove data objects (discussed in [the following chapter](#update-a-data-package)).

```{r, eval = FALSE}
update <- publish_update(adc_test, 
                         metadata_pid = pkg$metadata,
                         resource_map_pid = pkg$resource_map,
                         data_pids = pkg$data,
                         metadata_path = eml_path, 
                         public = FALSE)
```

Note that there are other arguments to `publish_update()` you may need.

After your package is published, run the `qa_package()` function from the `datamgmt` package. 

The function arguments are as follows:
```{r, eval=FALSE}
qa_package <- function(node, pid, readAllData = TRUE,
                       check_attributes = TRUE,
                       check_creators = FALSE,
                       check_access = FALSE)
```

By default, `qa_package()` checks for:

* Correctness of distribution URLs for each data object (URLs must match the EML physical section for the object)
* Congruence of metadata and data

The `check_creators` and `check_access` flags can be set to `TRUE` to check:

* Correctness of ORCIDs of creators in a given EML
* Rights and access are set for creators in the system metadata

In most cases, `qa_package()` will be run just by passing in a member node and the resource map PID.
```{r, eval=FALSE}
qa_package(mn, resource_map_pid)
```

## Exercise 3b {.exercise}
* Make sure you have everything from [before](#exercise-3a) in R.
* Validate, write and update your package using the respective functions.
* Use the <a href = 'https://nceas.github.io/datateam-training/reference/final-checklist-before-notifying-submitter.html' target='_blank'>checklist</a> to review your submission.
* Make edits where necessary, and publish updates as needed.
