# Editing EML

This chapter is a practical tutorial for using R to read, edit, write, and validate EML documents. Much of the information here can also be found in the vignettes for the R packages used in this section (e.g. the <a href = 'https://github.com/ropensci/EML/blob/master/vignettes/creating-EML.Rmd' target='_blank'>EML package</a>). 

Most of the functions you will see in this chapter will use the `arcticdatautils` and `EML` packages.

```{block, type = "note"}
This chapter will be longest of all the sections! This is a reminder to take frequent breaks when completing this section.
```

```{r, child = '../workflows/edit_eml/edit_an_eml_element.Rmd'}
```

## FAIR data practices

The result of these function calls won't show up on the webpage but they will add a `publisher` element to the `dataset` element and a `system` to all of the entities based on what the PID is. This will help make our metadata more FAIR (Findable, Accessible, Interoperable, Reusable). 

These two functions come from the `arcticatautils` package, an R package we wrote to help with some very specific data processing tasks.

Add these function calls to all of your EML processing scripts.

```{r, eval= FALSE}
  library(arcticdatautils)

  doc <- eml_add_publisher(doc)
  doc <- eml_add_entity_system(doc)
```

```{r, child = '../workflows/edit_eml/edit_attributelists.Rmd'}
```

```{block, type = "note"}
Remember to use:
`d1c_test <- dataone::D1Client("STAGING", "urn:node:mnTestARCTIC")`
`d1c_test@mn` 
```

```{r, child = '../workflows/edit_eml/set_physical.Rmd'}
```

```{r, child = '../workflows/edit_eml/edit_datatables.Rmd'}
```

```{r, child = '../workflows/edit_eml/edit_otherentities.Rmd'}
```

```{r, child = '../workflows/edit_eml/edit_semantic_annotation.Rmd'}
```

## Exercise 3a {.exercise}

The metadata for the dataset created earlier in Exercise 2 was not very complete. Here we will add a attribute and physical to our entity (the csv file).

* Make sure your package from [before](#exercise-2) is loaded into R.
* Convert `otherEntity` into `dataTable`.
* Replace the existing `dataTable` with a new `dataTable` object with an `attributelist` you write in R using the above commands.
* We will continue using the objects created and updated in this exercise in 3b.

Below is some pseudo-code for how to accomplish the above steps. Fill in the dots according to the above sections to complete the exercise.

```
dp # print the value of dp to ensure it is still in your environment

# get metadata pid
mo <- selectMember(...)

# read in EML
doc <- read_eml(getObject(...))

# convert otherEntity to dataTable
doc <- eml_otherEntity_to_dataTable(...)

# write an attribute list using shiny_attributes based on the data in your file
ex_data <- read.csv(...)
atts <- shiny_attributes(data = ex_data)

# set the attributeList
doc$dataset$dataTable$attributeList <- set_attributes(...)

```


## Validate EML and update package

To make sure that your edited EML is valid against the EML schema, run `eml_validate()` on your EML. Fix any errors that you see.

```{r, eval = F}
eml_validate(doc)
```

You should see something like if everything passes:
>[1] TRUE
>attr(,"errors")
>character(0)

Then save your EML to a path of your choice or a temp file. You will later pass this path as an argument to update the package.

```{r, eval = F}
eml_path <- "path/to/save/eml.xml"
write_eml(doc, eml_path)
```


## Exercise 3b {.exercise}

* Make sure you have everything from [before](#exercise-3a) in R.

After adding more metadata, we want to publish the dataset onto `test.arcticdata.io`. Before we publish updates we need to do a couple checks before doing so.

* Validate your metadata using `eml_validate`.
* Use the [checklist](#final-checklist) to review your submission.
* Make edits where necessary

Once `eml_validate` returns `TRUE` go ahead and run `write_eml`, `replaceMember`, and `uploadDataPackage`. There might be a small lag for your changes to appear on the website. This part of the workflow will look roughly like this:

```
# validate and write the EML
eml_validate(...)
write_eml(...)

# replace the old metadata file with the new one in the local package
replaceMember(dp, ...)

# upload the data package
packageId <- uploadDataPackage(...)
```

