# Editing EML

This chapter is a practical tutorial for using R to read, edit, write, and validate EML documents. Much of the information here can also be found in the vignettes for the R packages used in this section (e.g. the <a href = 'https://github.com/ropensci/EML/blob/master/vignettes/creating-EML.Rmd' target='_blank'>EML package</a>).

```{block, type = "note"}
This chapter will be longest of all the sections! This is a reminder to take frequent breaks when completing this section.
```

```{r, child = '../workflows/edit_data_packages/get_package_and_eml.Rmd'}
```

```{r, child = '../workflows/edit_eml/edit_an_eml_element.Rmd'}
```

```{r, child = '../workflows/edit_eml/edit_attributelists.Rmd'}
```

```{r, child = '../workflows/edit_eml/set_physical.Rmd'}
```

```{r, child = '../workflows/edit_eml/edit_datatables.Rmd'}
```

```{r, child = '../workflows/edit_eml/edit_otherentities.Rmd'}
```

## Exercise 3a {.exercise}

* Make sure your package from [before](#exercise-2) is loaded into R.
* Replace the existing `dataTable` with a new `dataTable` object with an `attributelist` and `physical` section you write in R using the above commands.
* We will continue using the objects created and updated in this exercise in 3b

```{r, child = '../workflows/edit_eml/edit_spatialvectors.Rmd'}
```

```{r, child = '../workflows/edit_eml/set_coverages.Rmd'}
```

```{r, child = '../workflows/edit_eml/set_methods.Rmd'}
```

```{r, child = '../workflows/edit_eml/set_parties.Rmd'}
```

## Validate EML and update package

To make sure that your edited EML is valid against the EML schema, run `eml_validate()` on your EML. Fix any errors that you see.

```{r, eval = F}
eml_validate(doc)
```

You should see something like if everything passes:
>[1] TRUE
>attr(,"errors")
>character(0)

Then save your EML to a path of your choice or a temp file. You will later pass this path as an argument to update the package.

```{r, eval = F}
eml_path <- "path/to/save/eml.xml"
write_eml(doc, eml_path)
```



To update a package with the newly edited EML, use `arcticdatautils::publish_update()`. This function has an argument for adding data `PID`s (or otherwise including existing data `PID`s) to make sure that they stay with the package. This function allows you to make metadata edits, as well as add or remove data objects (discussed in [the following chapter](#update-a-data-package)).

```{r, eval = FALSE}
update <- publish_update(adc_test, 
                         metadata_pid = pkg$metadata,
                         resource_map_pid = pkg$resource_map,
                         data_pids = pkg$data,
                         metadata_path = eml_path, 
                         public = FALSE)
```

Note that there are other arguments to `publish_update()` you may need.

After your package is published, run the `qa_package()` function from the `datamgmt` package. 

The function arguments are as follows:
```{r, eval=FALSE}
qa_package <- function(node, pid, readAllData = TRUE,
                       check_attributes = TRUE,
                       check_creators = FALSE,
                       check_access = FALSE)
```

By default, `qa_package()` checks for:

* Correctness of distribution URLs for each data object (URLs must match the EML physical section for the object)
* Congruence of metadata and data

The `check_creators` and `check_access` flags can be set to `TRUE` to check:

* Correctness of ORCIDs of creators in a given EML
* Rights and access are set for creators in the system metadata

In most cases, `qa_package()` will be run just by passing in a member node and the resource map PID.
```{r, eval=FALSE}
qa_package(mn, resource_map_pid)
```

## Exercise 3b {.exercise}

* Make sure you have everything from [before](#exercise-3a) in R.
* Validate, write and update your package using the respective functions.
* Use the <a href = 'https://nceas.github.io/datateam-training/reference/final-checklist-before-notifying-submitter.html' target='_blank'>checklist</a> to review your submission.
* Make edits where necessary, and publish updates as needed.


## General tips for dealing with data packages

In this section, we'll be discussing the general guidelines when dealing with data packages - specifically, when to touch a PI's data, what constitutes as a robust and comprehensive methods/abstract section, and when it is necessary to followup with PIs about dataset and metadata inquiries.

One of the biggest dilemmas when handling data packages is deciding when it's appropriate to touch a PI's data. As a rule of thumb, data entries themselves should always be fixed. Our goal is to clean-up the files, not to revise the data. 

Data file conversions are generally alright. Conversions are needed when the existing file format may become unavailable in the future. In the case of Excel sheets, since they are stored in a proprietary software, the files may eventually become inaccessible. Storing them in a non-proprietary software, such as a csv or text file, prevents it from becoming extinct. 

Data files should also be revised if there are formatting issues. For instance, column headers should be fixed if there exists special characters, spaces, etc. Similarly, if there exists blank entries without missing value codes, they should be filled in with `NA` values with their respective explanations. These changes should be documented somewhere in the description or in an attribute definition.

Finally, altered data files should be linked to the originals through provenance. 

When it comes to methods, the information is sufficient when a reasonable scientist can interpret the data and replicate the study without consulting the PI nor any other resources. Enough information should be provided such that users can understand how the data were collected, how to interpret the values, and potentially how to use the data in the case of specialized files. The abstract should provide an overview of the scientific project, how the data package fits into the larger project, a synopsis of the experimental or sampling design, and a summary of the data contents. 

If either of these sections are insufficient, the PI should be contacted for revisions. In the case that the project is funded by an NSF grant, a missing/insufficient abstract can be replaced by the abstract provided on the NSF funding page.

An exception to the methods/abstract guidelines would be if the data package has a parent that it will eventually be nested under. If the parent contains a comprehensive abstract and methods, then the individual data packages can have more brief information.
