# Editing EML

This chapter is a practical tutorial for using R to read, edit, write, and validate EML documents. Much of the information here can also be found in the vignettes for the R packages used in this section (e.g. the <a href = 'https://github.com/ropensci/EML/blob/master/vignettes/creating-EML.Rmd' target='_blank'>EML package</a>). 

Most of the functions you will see in this chapter will use the `arcticdatautils` package.

```{block, type = "note"}
This chapter will be longest of all the sections! This is a reminder to take frequent breaks when completing this section.
```

```{r, child = '../workflows/edit_eml/edit_an_eml_element.Rmd'}
```

## FAIR data practices

The result of these function calls won't show up on the webpage but they will add a `publisher` element to the `dataset` element and a `system` to all of the entities based on what the PID is. This will help make our metadata more FAIR (Findable, Accessible, Interoperable, Reusable). 

Add the following lines to all of your data processing scripts.
```{r, eval= FALSE}
  doc <- eml_add_publisher(doc)
  doc <- eml_add_entity_system(doc)
```

```{r, child = '../workflows/edit_eml/edit_attributelists.Rmd'}
```

```{r, child = '../workflows/edit_eml/set_physical.Rmd'}
```

```{r, child = '../workflows/edit_eml/edit_datatables.Rmd'}
```

```{r, child = '../workflows/edit_eml/edit_otherentities.Rmd'}
```

```{r, child = '../workflows/edit_eml/edit_semantic_annotation.Rmd'}
```

## Exercise 3a {.exercise}

The metadata for the dataset created earlier in Exercise 2 was not very complete. Here we will add a attribute and physical to our entity (the csv file).

* Make sure your package from [before](#exercise-2) is loaded into R.
* Convert `otherEntity` into `dataTable`.
* Replace the existing `dataTable` with a new `dataTable` object with an `attributelist` and `physical` section you write in R using the above commands.
* Add semantic annotations for attribute area.
* We will continue using the objects created and updated in this exercise in 3b.

```{r, child = '../workflows/edit_eml/edit_spatialdata.Rmd'}
```

```{r, child = '../workflows/edit_eml/set_coverages.Rmd'}
```

```{r, child = '../workflows/edit_eml/set_methods.Rmd'}
```

```{r, child = '../workflows/edit_eml/set_parties.Rmd'}
```

## Validate EML and update package

To make sure that your edited EML is valid against the EML schema, run `eml_validate()` on your EML. Fix any errors that you see.

```{r, eval = F}
eml_validate(doc)
```

You should see something like if everything passes:
>[1] TRUE
>attr(,"errors")
>character(0)

Then save your EML to a path of your choice or a temp file. You will later pass this path as an argument to update the package.

```{r, eval = F}
eml_path <- "path/to/save/eml.xml"
write_eml(doc, eml_path)
```



To update a package with the newly edited EML, use `arcticdatautils::publish_update()`. This function has an argument for adding data `PID`s (or otherwise including existing data `PID`s) to make sure that they stay with the package. This function allows you to make metadata edits, as well as add or remove data objects (discussed in [the following chapter](#update-a-data-package)).

```{r, eval = FALSE}
update <- publish_update(adc_test, 
                         metadata_pid = pkg$metadata,
                         resource_map_pid = pkg$resource_map,
                         data_pids = pkg$data,
                         metadata_path = eml_path, 
                         public = FALSE)
```

Note that there are other arguments to `publish_update()` you may need.

After your package is published, run the `qa_package()` function from the `datamgmt` package. 

The function arguments are as follows:
```{r, eval=FALSE}
qa_package <- function(node, pid, readAllData = TRUE,
                       check_attributes = TRUE,
                       check_creators = FALSE,
                       check_access = FALSE)
```

By default, `qa_package()` checks for:

* Correctness of distribution URLs for each data object (URLs must match the EML physical section for the object)
* Congruence of metadata and data

The `check_creators` and `check_access` flags can be set to `TRUE` to check:

* Correctness of ORCIDs of creators in a given EML
* Rights and access are set for creators in the system metadata

In most cases, `qa_package()` will be run just by passing in a member node and the resource map PID.
```{r, eval=FALSE}
qa_package(mn, resource_map_pid)
```

```{block, type = "note"}
There is a bug in for `qa_package()` for datasets in test.arcticdata.io that should be ignored:
```
```
The distribution URL for object urn:uuid:......(your resource map pid) is missing or incongruent in the physical section of the EML.
Error in dl_and_read_all_data(mn, package, doc, read_all_data) : 
All distribution URLs for data objects must match the data PIDs to continue.
```


## Exercise 3b {.exercise}

* Make sure you have everything from [before](#exercise-3a) in R.

After adding more metadata, we want to publish the dataset onto `test.arcticdata.io`. Before we publish updates we need to do a couple checks before doing so.

* Validate your metadata using `eml_validate`.
* Use the [checklist](#final-checklist) to review your submission.
* Make edits where necessary

Once `eml_validate` returns `TRUE` go ahead and run `write_eml` and `publish_update`. There might be a small lag for your changes to appear on the website. 
