# Edit EML in R

This chapter is a practical tutorial for using R to read, edit, write, and validate EML documents. Much of the information here can also be found in the vignettes for the R packages used in this section (e.g. the [EML package](https://github.com/ropensci/EML/blob/master/vignettes/creating-EML.Rmd)).

```{r, child = '../workflows/edit_data_packages/get_package_and_eml.Rmd'}
```

```{r, child = '../workflows/edit_eml/edit_an_eml_element.Rmd'}
```

```{r, child = '../workflows/edit_eml/edit_attributelists.Rmd'}
```

```{r, child = '../workflows/edit_eml/set_physical.Rmd'}
```

```{r, child = '../workflows/edit_eml/edit_datatables.Rmd'}
```

```{r, child = '../workflows/edit_eml/edit_otherentities.Rmd'}
```

```{r, child = '../workflows/edit_eml/edit_spatialvectors.Rmd'}
```

```{r, child = '../workflows/edit_eml/set_coverages.Rmd'}
```

```{r, child = '../workflows/edit_eml/set_methods.Rmd'}
```

```{r, child = '../workflows/edit_eml/set_parties.Rmd'}
```

## Validate your EML and update the data package

To make sure that your edited EML is valid against the EML schema, run `eml_validate` on your EML. Fix any errors that you see, and then save your EML to a path of your choice or a temp file. You will later pass this path as an argument to update the package.

```{r, eval = F}
eml_validate(eml)
eml_path <- "path/to/save/eml.xml"
write_eml(eml, eml_path)
```

To update a package with the newly edited EML, use `arcticdatautils::publish_update`. This function has an argument for adding data `PID`s (or otherwise including existing data `PID`s) to make sure that they stay with the package. This function allows you to make metadata edits, as well as add or remove data objects (discussed in [the following chapter](#update-a-data-package)).

```{r, eval = FALSE}
update <- publish_update(adc_test, 
                         metadata_pid = pkg$metadata,
                         resource_map_pid = pkg$resource_map,
                         data_pids = pkg$data,
                         metadata_path = eml_path, 
                         public = FALSE)
```

Note that there are other arguments to `publish_update` you may need.

## SASAP package workflows
Sometimes many data sets are associated with a larger project, such as the State of Alaska Salmon and People (SASAP) project. These data sets should be given additional project-specific information using `eml@dataset@project`. This will add pre-defined information including the project title, funding sources, and key personnel. You will also want to set access permissions to the project as well. If you are working on a SASAP data set, prior to writing the EML and publishing the data set you will set the project with this code:

```{r, eval=FALSE}
source('/home/eodean/sasap-data/data-submission/Helpers/SasapProjectCreator.R')
eml@dataset@project <- sasap_project()
```

Next you should add SASAP-specific taxonomic coverage to the EML using the `add_sasap_taxa` function.  This will ensure that any salmon species present in the dataset have their Latin and common names listed in the coverage and can be easily searched for. 
  
```{r, eval=FALSE}
source('/home/dmullen/sasap-helpers/add_sasap_taxa.R')
eml <- add_sasap_taxa(mn, eml)
```

Then, update the access permissions in the system metadata using `set_rights_and_access`.

```{r, eval=FALSE}
pkg <- get_package(mn, resource_map_pid)
set_rights_and_access(mn, unlist(pkg), 'CN=SASAP,DC=dataone,DC=org', permissions = c('read', 'write', 'changePermission'))
```

Finally, go through the [SASAP checklist](https://github.nceas.ucsb.edu/NCEAS/sasap-data/blob/master/data-submission/checklist.Rmd) to ensure that the package meets all of the project-specific requirements for publishing.

After your package is published, run the `qa_package()` function from the `datamgmt` package. 

The function arguments are as follows:
```{r, eval=FALSE}
qa_package <- function(node, pid, readAllData = TRUE,
                       check_attributes = TRUE,
                       check_creators = FALSE,
                       check_access = FALSE)
```

By default, `qa_package` checks for:
- Correctness of distribution URLs for each data object (URLs must match the EML physical section for the object)
- Congruence of metadata and data 

The `check_creators` and `check_access` flags can be set to `TRUE` to check: 
- Correctness of ORCIDs of creators in a given EML
- Rights and access are set for creators for a give pid sysmeta

In most cases, QA package will be run just by passing in a member node and the resource map pid.
```{r, eval=FALSE}
qa_package(mn, resource_map_pid)
```

Note that there are some issues with the function that are documented [here](https://github.com/NCEAS/datamgmt/issues/145). 

## Exercise 3 {.exercise}
* Make sure your package from [before](#exercise-2) is loaded into R.
* Replace the existing `dataTable` with a new `dataTable` object with an `attributelist` and `physical` section you write in R using the above commands.
* Then write, validate, and update your package.
* Use the [checklist](https://nceas.github.io/datateam-training/reference/final-checklist-before-notifying-submitter-pi.html) to review your submission.
* Make edits where necessary, and publish updates as needed.
 
 
