# Updating a data package

This chapter will teach you how to edit and update an existing data package in R. Earlier, we updated metadata. In this section we will learn how to update a data file, and how to update a package by adding an additional data file.

```{r, child = '../workflows/edit_data_packages/update_an_object.Rmd'}
```

```{r, child = '../workflows/edit_data_packages/update_a_package.Rmd'}
```

## Exercise 4 {.exercise}

What if the researcher notices that some information needed to be updated in the data file? We can use `update_object` to do just that!

If you haven't already:

* Locate the data package you published in the [previous exercise](#exercise-3b) by navigating to the URL test.arcticdata.io/#view/...
* Load the package and EML into R using the above commands.

Make a slightly different data file to upload to `test.arcticdata.io` for this exercise:

* Load the data file associated with the package into R as a `data.frame`. (Hint: use `read.csv()` to upload the data file from your computer/the server.)
* Make an edit to the data in R (e.g. change one of the colnames to `"TEST"`).
* Save the edited data. (Hint: use `write.csv(data, row.names = FALSE)`.)

Upload the new csv file, get a new pid and publish those updates:

* Update the data file in the package with the edited data file using `update_object`.
* Update your package using `publish_update`.
