# First Ticket

After completing the previous chapters, Jasmine or Jeanette will assign a ticket from RT. Login using your LDAP credentials got get familiarized with RT.

```{r, child = '../workflows/pi_correspondence/navigate_rt.Rmd'}
```

Before opening a R script first look over the initial checklist first to identify what you will need to update in the metadata.

```{r, child = '../workflows/pi_correspondence/initial_review_checklist.Rmd'}
```

## Processing templates

We have developed some partially filled R scripts to get you started on working on your first dataset. They outline common functions used in processing a dataset. However, it will differ depending on the dataset.

You can use this template where you can [fill in the blanks](data/dataset_processing_example_blanks.R) to get familiar with the functions we use and workflow at first. We also have a more minimal example [A filled example](data/dataset_processing_example_skeleton.R) as a intermediate step. You can look at the [filled example](data/dataset_processing_example_filled.R) if you get stuck or message the #datateam.

Once you have updated the dataset to your satisfaction and reviewed the Final Checklist, post the link to the dataset on #datateam for peer review.

```{r, child = '../workflows/pi_correspondence/final_review_checklist.Rmd'}
```

After all the revisions send the link to the PI in an email through RT. Send the draft of the email to Jasmine or Jeanette on Slack.
```{r, child = '../workflows/pi_correspondence/A_email_templates.Rmd'}
```

Once the dataset is approved by the PI and there are no further changes, publish the dataset with a doi.
```{r, eval=F}
update <- publish_update(adc,
                         metadata_pid = pkg$metadata,
                         data_pids = pkg$data,
                         resource_map_pid = pkg$resource_map,
                         metadata_path = eml_path,
                         public = T,
                         use_doi = T)
```

## Categorize datasets

As a final step we will categorize the dataset you processed. We are trying to categorize datasets so we can have a rough idea of what kinds of datasets we have at the Arctic Data Center. We will grant you access to the google sheet that has all of the [categorized  datasets](https://docs.google.com/spreadsheets/d/1S_7iW0UBZLZoJBrHXTW5fbHH-NOuOb6xLghraPA4Kf4/edit#gid=1479370118)

We will categorize each dataset into one of the predefined themes (ie. biology, ecology etc.). Definition of the themes can be found in the [google sheet](https://docs.google.com/document/d/1rqHk9SCH9JvdSnIJovYVE1YF4IF4_yNxFfCOJMI8xjk/edit)

Run the following line with your doi and themes as a list.

```{r, eval=F}
datamgmt::categorize_dataset("you_doi", c("list", "of", "themes"), "your name")
```

## Congrats!

Congratulations on finishing your first ticket! You can head over to the the repository, [data-processing](https://github.com/NCEAS/data-processing) to get your ticket processing code reviewed by the team so we can learn from each other!
