# Introduction to Solr

Solr is what's known as an index, which helps us keep track of objects stored in our metadata catalog ([Metacat](https://www.dataone.org/software-tools/metacat)).

Every object in Metacat has a corresponding Solr document for it that contains information about that object.
Each type of Object will have a different set of fields in its Solr document. For example, an EML document will have a `title` field (corresponding to the EML document's `<title>` element), while a CSV will not.

The fields that go into a Solr document are populated by information such as:

- The system metadata (fileName, accessPolicy, etc)
- The object itself (e.g. title, creators, etc. for an EML record)
- Additional computed fields (e.g., a geohash for quick spatial search)

Indexing the Object's Metacat stores lets us execute some interesting and very useful queries such as:

- What are the most recently updated datasets?
- What Metadata and Data Objects are in a given Data Package?
- What is the total size (in terms of disk space) of all Objects stored in Metacat?

Querying Solr is possible [by tacking a query onto a base URL](#query-solr) or [through the `dataone::query()` function in R](#query-solr-through-R). For now, we'll just cover the basics of Solr queries in R. See the [Data Team References](https://nceas.github.io/datateam-training/reference/query-with-solr.html) for more on Solr.

```{r, child = '../workflows/query_with_solr/construct_a_query.Rmd'}
```

```{r, child = '../workflows/query_with_solr/query_solr_through_R.Rmd'}
```
