# Introduction to Solr

Solr is what's known as an index, which helps us keep track of the data, metadata, and resource map objects stored in our metadata catalog, [Metacat](https://www.dataone.org/software-tools/metacat).

Solr allows you to quickly search through any coordinating or member node. Some more common use-cases include:

- Recovering lost pids - if you publish new data objects ([`publish_object`](https://nceas.github.io/datateam-training/training/create-data-packages-in-r.html#publish-an-object)) but forget to save the pids, you can recover them with a query. For example, you can search for all data objects that are not associated with a resource map _and_ are published using your ORCID (`q=-resourceMap:*+AND+submitter:*XXXX-YYYY-ZZZZ-WWWW`)
- Working with groups of packages - if you want to find all data, metadata, and resource maps associated with a PI, you can use `q=origin:*SURNAME*` or perhaps `q=rightsHolder:*XXXX-YYYY-ZZZZ-WWWW`

Once you understand the logic of queries, it becomes a flexible tool that can be used to answer a variety of interesting and useful questions, for example: 

- What are the most recently updated datasets?
- What metadata and data objects are in a given data package?
- What is the total size (in terms of disk space) of all objects stored in Metacat?

Querying Solr is possible [by tacking a query onto a base URL](https://nceas.github.io/datateam-training/reference/query-solr-via-a-browser.html) or [through the `dataone::query()` function in R](https://nceas.github.io/datateam-training/training/introduction-to-solr.html#query-solr-through-r). For now, we'll just cover the basics of Solr queries in R. See the [Data Team References](https://nceas.github.io/datateam-training/reference/solr-queries.html) for more on Solr.

```{r, child = '../workflows/solr_queries/construct_a_query.Rmd'}
```

```{r, child = '../workflows/solr_queries/query_solr_through_R.Rmd'}
```
