# Beyond your first ticket

This section is meant to be read after you have processed a couple of tickets and you are comfortable with the workflow with a relatively simple dataset with 1-2 files and want to expand your skills and workflows further.

## Working with large data packages

```{r, child = '../workflows/adc_web_submissions/add_physicals_to_submissions.Rmd'}
```

```{r, child = '../workflows/edit_eml/use_references.Rmd'}
```

## Annotations

If there are multiple tables with similar annotations you can try something like this:

```{r, eval = F}
#go through each dataTable
for(i in 1:length(doc$dataset$dataTable)){
  
  #get all the attibute names
  an <- eml_get_simple(doc$dataset$dataTable[[i]], "attributeName")
  
  #go through the attributes figure out what will match
  for(a in 1:length(an)){
    annotation <- dplyr::case_when(
      # the attributeName to match ~ valueLabel
      an[[a]] == "Sample ID" ~ "Identity",
      an[[a]] == "Location" ~ "study location name",
      an[[a]] == "Latitude" ~ "latitude coordinate",
      an[[a]] == "Longitude" ~ "longitude coordinate",
      an[[a]] == "Elevation (m)" ~ "elevation",
      str_detect(an[[a]], "Depth|depth") ~ "Depth")
    
    #only run this code when the annotations match
    if(!is.na(annotation)){
      #based on the entity Name create a unique id
      entity <- str_split(doc$dataset$dataTable[[i]]$entityName, "_")
      doc$dataset$dataTable[[i]]$attributeList$attribute[[a]]$id <- paste0(entity[[1]][[1]], "_", an[[a]])
      
      #add the annotation
      doc$dataset$dataTable[[i]]$attributeList$attribute[[a]]$annotation <- eml_ecso_annotation(annotation)
    }
  }
  
}
```

## Streamlining your workflow

```{r, child = '../workflows/miscellaneous/code_snippets.Rmd'}
```

```{r, child = '../workflows/miscellaneous/resources_for_r.Rmd'}
```
