## Publishing an Object {#Publishing_an_Object}

Objects (data files, xml metadata files) can be published to a DataONE node using the function `arcticdatautils::publish_object`. 

To publish a metadata file you can use the following call:
```{r, eval = FALSE}
meta_path <- 'path/to/your/metadata/metadata.xml'
metadata_pid <- arcticdatautils::publish_object(mn, meta_path, format_id = format_eml())
```

This call will save the id of the metadata object to the variable `pid`, which you will need later for the resource map. It also adds a formatID, which identifies what kind of object you just uploaded. Similarly, you can publish data objects like this:

```{r, eval = FALSE}
data_path <- 'path/to/your/data/data.csv'
data_pid <- arcticdatautils::publish_object(mn, data_path, format_id = 'text/csv')
```

Note that you will need to be explicit about your `format_id` here based on the file type. A list of format IDs can be found [here on the DataONE website](https://cn.dataone.org/cn/v2/formats).

After publishing the object, the object will need to be added to a `resource_map` by [updating](#Update_a_Package) or [creating](#Create_a_Resource_Map) a `resource_map`. Additionally, the [rights and access](#Set_Rights_and_Access) for the object must be set.

