## Add physicals to submissions

New submissions made through the web editor will not have any `physical` sections within the `otherEntity`s. Add them to the EML with the following script:
    
```{r, eval = FALSE}
for (i in seq_along(doc$dataset$otherEntity)) {
    otherEntity <- doc$dataset$otherEntity[[i]]
    id <- otherEntity$id
    
    if (!grepl("urn-uuid-", id)) {
        warning("otherEntity ", i, " is not a pid")
        
    } else {
        id <- gsub("urn-uuid-", "urn:uuid:", id)
        physical <- arcticdatautils::pid_to_eml_physical(mn, id)
        doc$dataset$otherEntity[[i]]$physical <- physical
    }
}
```

As you can see from code above, we use a for loop here to add `physical` sections. The for loop is a very useful tool to iterate over a list of elements. With for loop, you can repeat a specific block of code without copying and pasting the code over and over again. When processing datasets in Arctic Data Center, there are many places where for loop can be used, such as publishing a bunch of objects with pids, updating formatID for pkg$data, adding `physical` section like above code, etc.

To write out a for loop, you need a sequence part and body part. The sequence part usually generates indices to locate elements and the body part contains the code that you want to iterate for each element. 

Here is an example of adding `attribute` section within `dataTable`s using for loop. 
```{r, eval=F}
attributes <- read.csv('attributes.csv')  # attribute table in csv format downloaded from shiny app
attributeList <- EML::set_attributes(attributes = attributes)

for (i in 1:length(doc$dataset$dataTable)) { # sequence part
    doc$dataset$dataTable[[i]]$attributeList <- attributeList # body part
}
```
