## Create a new data package
*adapted from the dataone and datapack vingettes*

```{r , eval = F}
library(dataone)
library(datapack)
library(uuid)
```

Create a new data package
 - data package is a class that has slots for `relations` (provenance), `objects`(the metadata and data file(s)) and `systemMetadata`.
```{r, eval = F}
dp <- new("DataPackage")
```

### Upload new data files

#### Create and add a metadata file

In this example we will use this previously written EML metadata. Here we are getting the file path from the dataone package and saving that as the object `emlFile`.

This is a bit of an unusual way to reference a local file path, but all this does is looks within the R package `dataone` and grabs the path to a metadata document stored within that package. If you print the value of `emlFile` you'll see it is just a file path, but it points to a special place on the server where that package is installed. Usually you will just reference EML paths that are stored within your user file system.

```{r, eval = F}
emlFile <- system.file("extdata/strix-pacific-northwest.xml", package="dataone")
```

Create a new `DataObject` and add it to the package.
```{r, eval = F}
metadataObj <- new("DataObject", format="https://eml.ecoinformatics.org/eml-2.2.0", filename=emlFile)
dp <- addMember(dp, metadataObj)
```

Check the dp object to see if the `DataObject` was added correctly.
```{r, eval = F}
dp
```

#### Add some additional data files
```{r, eval = F}
sourceData <- system.file("extdata/OwlNightj.csv", package="dataone")
sourceObj <- new("DataObject", format="text/csv", filename=sourceData)
dp <- addMember(dp, sourceObj, metadataObj)
```

#### Add additional files with structure

In this example adding the csv files to a folder named data and scripts
```{r, eval = F}
outputData <- system.file("extdata/Strix-occidentalis-obs.csv", package="dataone")
outputObj <- new("DataObject", format="text/csv", filename=outputData, targetPath = "data")
dp <- addMember(dp, outputObj, metadataObj)

progFile <- system.file("extdata/filterObs.R", package="dataone")
progObj <- new("DataObject", format="application/R", filename=progFile, targetPath = "scripts",
               mediaType="text/x-rsrc")
dp <- addMember(dp, progObj, metadataObj)
```

```{block, type = "note"}
If you want to change the formatId please use `updateSystemMetadata`
```

### Upload the package

```{r, eval = F}
d1c <- dataone::D1Client("STAGING", "urn:node:mnTestARCTIC")
```

Make sure to give access privlidges to the ADC admins:
```{r}
myAccessRules <- data.frame(subject="CN=arctic-data-admins,DC=dataone,DC=org", permission="changePermission") 
```

Get necessary token from test.arcticdata.io to upload the dataset prior uploading the datapackage:
```{r, eval = F}
packageId <- uploadDataPackage(d1c, dp, public=TRUE, accessRules=myAccessRules, quiet=FALSE)
```
