## Edit sysmeta

To edit the sysmeta of an object with a `pid` (data, metadata, resource_map, etc.) first load the sysmeta into R using the following command.

```{r, eval = FALSE}
sysmeta <- dataone::getSystemMetadata(mn, pid)
```

Then edit the sysmeta slots by using `@` functionality. For example, to change the `fileName` use the following command.

```{r , eval = FALSE}
sysmeta@fileName <- 'New File Name.csv'
```

Note that some slots cannot be changed by simple text replace (particularly the `accessPolicy`). There are various helper functions for changing the `accessPolicy` and `rightsHolder` such as `datapack::addAccessRule` (which takes the sysmeta as an input) or [`arcticdatautils::set_rights_and_access`](#set-rights-and-access), which only requires a PID. In general, you most frequently need to use `dataone::getSystemMetadata` to change either the `formatId` or `fileName` slots.

After you have changed the necessary slot, you can update the system metadata using the following command.

```{r, eval = FALSE}
updateSystemMetadata(mn, pid, sysmeta)
```

### Identifiers and sysmeta

Importantly, changing the system metadata does NOT necessitate a change in the PID of an object. This is because changes to the system metadata do not change the object itself, they are only changing the description of the object (although ideally the system metadata is accurate when an object is first published). 