## Get package and EML

Before we look more in depth at EML, we first need to load your data package into R. After [setting your node](https://nceas.github.io/datateam-training/reference/set-dataone-nodes.html), use the following commands to load the package:

```{r, eval = FALSE}
rm_pid <- "your_resource_map_pid"

pkg <- get_package(adc_test,
                   rm_pid,
                   file_names = TRUE)
```

```{block, type = "note"}
**Keeping track of PIDs**

In all subsequent sections, if they ask for the `pid` of the metadata, reasource map or data you can refer to the object from `get_package()`. 

For example, if you assigned the value from `get_package()` as above as `pkg` then you can refer to the following by using the corresponding commands:
```

```{r, eval= FALSE}
metadata_pid <-  pkg$metadata
data_pid <-  pkg$data
reasource_pid <-  pkg$reasource_map
```

After loading the package, you can also load the EML file into R using the following command:

```{r, eval = FALSE}
doc <- read_eml(getObject(adc_test, pkg$metadata))
```

Note that we named the object `doc`. This is a good generic name to use for EML documents. The generic name `eml` should not be used - as the EML package ships with an `eml` function, which can cause namespace issues in your environment if you have an object also called `eml`.

```{block, type = 'note'}
**Tip to always have the most recent resource map.**

When editing data packages, you always want to be working with the most recent update. To ensure you have the most recent resource map, you can use the following commands:

<pre class="sourceCode r"><code class="sourceCode r">rm_pid_original &lt;-<span class="st"> &quot;your_original_resource_map_pid&quot;</span>
all_rm_versions &lt;-<span class="st"> </span><span class="op"></span><span class="kw">get_all_versions</span>(adc_test, rm_pid_original)
rm_pid &lt;-<span class="st"> </span>all_rm_versions[<span class="kw">length</span>(all_rm_versions)]
print(rm_pid)</code></pre>
```

```{r, eval = FALSE, echo = FALSE}
# Code used to generate HTML in note above
rm_pid_original <- "your_original_resource_map_pid"
all_rm_versions <- get_all_versions(adc_test, rm_pid_original)
rm_pid <- all_rm_versions[length(all_rm_versions)]
print(rm_pid)
```
