## Obsolescence chain

You can obsolete a dataset using the function `datamgmt::obsolete_package()`. Use the documentation for instructions on using the function. The following workflow explains how the functions operate.
  
This chunk is to obsolete one data set. If there are more to add to the chain, more steps can be added. Be very careful. Make sure to fill in `obsoletes` and `obsoletedBy` slots for each one.  The `obsoletes` and `obsoletedBy` fields must be `NA`, once they are populated they can't be modified.  

```{r, eval = FALSE}
# get oldest version of the file you want to be visible. Use get_all_versions and look at the latest.
# urn:uuid:...

# PID for data set to be obsoleted (hidden): doi:10…

# adding data set to obsolete (hide) in the slot before the first version of the visible data set
sysmeta1 <- getSystemMetadata(mn, "urn:uuid:example_pid")
sysmeta1@obsoletes <- "doi:10.example_doi"
updateSystemMetadata(mn, "urn:uuid:example_pid", sysmeta1)

# adding first version to obsolescence chain after obsoleted (hidden) version
sysmeta0 <- getSystemMetadata(mn, "doi:10.example_doi")
sysmeta0@obsoletedBy <- "urn:uuid:example_pid"
updateSystemMetadata(mn, "doi:10.example_doi", sysmeta0)

```

The following code is equivalent to the code chunk above. This method is recommended, however it is necessary to read the function documentation first. 

```{r, eval = FALSE}
datamgmt::obsolete_package(mn, metadata_obsolete = "doi:10.example_doi", 
                           metadata_new = "urn:uuid:example_pid")
```
