## Publish an object

Objects (data files, xml metadata files) can be published to a DataONE node using the function `arcticdatautils::publish_object`. 
To publish an object, you must first get the `format_id` of the object you want to publish. A few common `format_ids` are listed below.

```{r, eval = FALSE}
# .csv file
format_id <- "text/csv"

# .txt file
format_id <- "text/plain"

# metadata file
format_id = format_eml()
```

Most objects have `format_ids` that can be found [here on the DataONE website](https://cn.dataone.org/cn/v2/formats). Metadata files (as shown above) use a special function to set the `format_id`. If the `format_id` is not listed at the DataONE website, you can set the `format_id <- NULL`.

Once you know the `format_id` you can publish your object using the commands below.

```{r, eval = FALSE}
path <- "path/to/your/file"
format_id <- "your/format_id"

pid <- arcticdatautils::publish_object(mnT,
                                       path = path,
                                       format_id = format_id)
```

After publishing the object, the `pid` will need to be added to a `resource_map` by [updating](#update-a-package) or [creating](#create-a-resource-map) a `resource_map`. Additionally, the [rights and access](#set-rights-and-access) for the object must be set.

