## Update an object

The `arcticdatautils::update_object` function updates a data object but does not change the resource map or EML. To simultaneously update all three parts of a data package, you can use the `datamgmt::update_package_object`.

The [`update_package_object`](https://nceas.github.io/datamgmt/reference/update_package_object.html) function updates a data object, and then automatically updates the package resource map with the new data `PID`. If an object already has a `dataTable` or `otherEntity` with a working `physical` section, the EML will be updated with the new data object’s `physical`.

To use, input the following arguments:

```{r eval = FALSE}
update_package_object(mnT,
                      data_pid = "the data PID you need to update", # pkg$data
                      new_data_path = "path/to/the/new/data.csv",
                      resource_map_pid = "resource map of the data package", # pkg$resource_map
                      format_id = "the formatId", # use line 2 (Id:) from https://cn.dataone.org/cn/v2/formats
                      public = FALSE,
                      use_doi = FALSE,
                      ...) #any other arguments to pass to publish_update (child_pids, etc)
```

To try it out for yourself, you can run this code to create a dummy package on [test.arctic.io](https://test.arctic.io) and update one of its objects.

```{r eval = FALSE}
#input token to run
cnT <- dataone::CNode('STAGING')
mnT <- dataone::getMNode(cnT,'urn:node:mnTestARCTIC')

pkg <- create_dummy_package2(mnT, title = "My package")

file.create("new_file.csv")
update_package_object(mnT, pkg$data[1], "new_file.csv", pkg$resource_map, format_id = "text/csv")
file.remove("new_file.csv") #clean up

#check out the package on test.arcticdata.io
```

```{block, type = "note"}
You will need to be explicit about your `format_id` here based on the file type. A list of format IDs can be found [here on the DataONE website](https://cn.dataone.org/cn/v2/formats).
Use line 2 (Id:) exactly, character for character.
```
