## Update a package

To update a package, use `publish_update`. This function has an argument for adding data `PID`s (or otherwise including existing data `PID`s to make sure that they stay with the package). This function allows you to add or remove data objects, and/or make metadata edits.

First make sure you have the package you want to update, [loaded into R](#get-package-and-eml).

### Updating metadata

If you need to make edits to the metadata, do so. Then write the `EML` metadata to a file.

``` {r, eval = F}
eml_path <- "path/to/metadata/science_metadata.xml"
write_eml(eml, eml_path)
```

Next verify the eml is valid.

``` {r, eval = F}
eml_validate(eml_path)
```

The above should return `TRUE` if the `EML` is valid. If it returns `FALSE`, fix the EML file, use `write_eml()` to save the fixed file, and retry.

### Updating data

If you need to make edits to the data, [do so](#update-an-object).

### Publish update

Finally, update your data package at the `Member Node`.

```{r, eval = FALSE}
update <- arcticdatautils::publish_update(mnT, 
                                          metadata_pid = pkg$metadata,
                                          resource_map_pid =pkg$resource_map,
                                          data_pids = pkg$data,
                                          child_pids = NULL,
                                          use_doi = FALSE, 
                                          metadata_path = eml_path, 
                                          public = FALSE,
                                          check_first = TRUE)
```

Refresh the landing page at test.arcticdata.io/#view/... for this package and then follow the "newer version" link to view the latest.

If a package is ready to be public, you can change the `public` argument in the `publish_update` call to `TRUE`.

If you want to publish with a DOI (Digital Object Identifier) instead of a UUID (Universally Unique Identifier), you can change the `use_doi` argument to `TRUE`. **This should only be done after the package is finalized and has been thoroughly reviewed!**

If the package has children change `child_pids` to `pkg$child_packages`.