## Update a package


Once you have updated the data objects and saved the metadata to a file, we can update the metadata and add the new `pid` to the resource map using `publish_update`.

To update a package, use `arcticdatautils::publish_update`. This function has an argument for adding data `PID`s (or otherwise including existing data `PID`s) to make sure that they stay with the package. This function allows you to add or remove data objects, and/or make metadata edits.

First make sure you have the package you want to update, [loaded into R](#get-package-and-eml) using `get_package`.

### Publish update

Now we can update your data package.

```{r, eval = F}
eml_path <- "path/to/your/saved/eml.xml"

pkg <- get_package(mnT, "resource_map_pid")
```

```{r, eval = FALSE}
update <- publish_update(mnT, 
                          metadata_pid = pkg$metadata,
                          resource_map_pid =pkg$resource_map,
                          data_pids = pkg$data,
                          metadata_path = eml_path, 
                          public = FALSE)
```

Note that there are other arguments to `publish_update` you may need.

If a package is ready to be public, you can change the `public` argument in the `publish_update` call to `TRUE`.

If you want to publish with a DOI (Digital Object Identifier) instead of a UUID (Universally Unique Identifier), you can change the `use_doi` argument to `TRUE`. **This should only be done after the package is finalized and has been thoroughly reviewed!**

If the package has children change `child_pids` to `pkg$child_packages`.

Refresh the landing page at test.arcticdata.io/#view/... for this package and then follow the "newer version" link to view the latest.