## Update a package with a new data object

Once you have updated the data objects and saved the metadata to a file, we can update the metadata and use `replaceMember` to update the package with the new metadata.

Make sure you have the package you want to update loaded into R using `dataone::getDataPackage()`.

### Publish update

Now we can update your data package to include the new data object. Assuming you have updated your data package earlier something like the below: 
```{r, eval = FALSE}
d1c_test <- dataone::D1Client("STAGING", "urn:node:mnTestARCTIC")
packageId <- "the resource map"

dp <- getDataPackage(d1c_test, identifier=packageId, lazyLoad=TRUE, quiet=FALSE)
metadataId <- selectMember(dp, name="sysmeta@formatId", value="https://eml.ecoinformatics.org/eml-2.2.0")

#some modification to the EML here

eml_path <- "path/to/your/saved/eml.xml"
write_eml(doc, eml_path)

dp <- replaceMember(dp, metadataId, replacement=eml_path)
```

You can then upload your data package:
```{r, eval = FALSE}
myAccessRules <- data.frame(subject="CN=arctic-data-admins,DC=dataone,DC=org", permission="changePermission") 
packageId <- uploadDataPackage(d1c_test, dp, public=FALSE, accessRules=myAccessRules, quiet=FALSE)
```

If a package is ready to be public, you can change the `public` argument in the `datapack::uploadDataPackage()` call to `TRUE`.

If you want to publish with a DOI (Digital Object Identifier) instead of a UUID (Universally Unique Identifier), you need to do this when replacing the metadata. **This should only be done after the package is finalized and has been thoroughly reviewed!**
```{r, eval = FALSE}
doi <- dataone::generateIdentifier(d1c_test@mn, "DOI")
dp <- replaceMember(dp, metadataId, replacement=eml_path, newId=doi)

newPackageId <- uploadDataPackage(d1c_test, dp, public=TRUE, quiet=FALSE)
```

If there is a pre-issued DOI (researcher requested the DOI for the publication first), please do the following:
```{r, eval = FALSE}
dp <- replaceMember(dp, metadataId, replacement=eml_path, newId="your pre-issued doi previously generated")

newPackageId <- uploadDataPackage(d1c_test, dp, public=TRUE, quiet=FALSE)
```

If the package has children, see how to do this using `arcticdatautils::publish_update` in the nesting section of the reference manual.

Refresh the landing page at test.arcticdata.io/#view/... for this package and then follow the "newer version" link to view the latest.
