## Update a package with a new data object

Once you have updated the data objects and saved the metadata to a file, we can update the metadata and add the new `pid` to the resource map using `publish_update()`.

Make sure you have the package you want to update, [loaded into R](#get-package-and-eml) using `get_package()`.

### Publish update

Now we can update your data package to include the new data object.

```{r, eval = F}
eml_path <- "path/to/your/saved/eml.xml"

pkg <- get_package(adc_test, "resource_map_pid")
```

```{r, eval = FALSE}
update <- publish_update(adc_test, 
                         metadata_pid = pkg$metadata,
                         resource_map_pid = pkg$resource_map,
                         data_pids = c(pkg$data, id_new), # delete existing pid to be updated and add new pid
                         metadata_path = eml_path, 
                         public = FALSE)
```

If a package is ready to be public, you can change the `public` argument in the `publish_update()` call to `TRUE`.

If you want to publish with a DOI (Digital Object Identifier) instead of a UUID (Universally Unique Identifier), you can change the `use_doi` argument to `TRUE`. **This should only be done after the package is finalized and has been thoroughly reviewed!**

If the package has children, set the `child_pids` argument to `pkg$child_packages`.

Refresh the landing page at test.arcticdata.io/#view/... for this package and then follow the "newer version" link to view the latest.
