## Edit attributeLists

Attributes are stored in an [attributeList](https://github.com/NCEAS/eml/blob/master/eml-attribute.png). When editing attributes in R, you need to create one-three objects:

1. A data.frame of attributes
2. A data.frame of custom units (if applicable)
3. A data.frame of factors (if applicable)

Note, to edit/examine an existing attribute table already in a eml file you can use the following commands. 

```{r, eval = FALSE}
attributeList <- EML::get_attributes(eml@dataset@dataTable[[i]]@attributeList)
attributes <- attributeList$attributes
```

### Edit Attributes

Attribute information should be stored in a `data.frame` with the following columns.

* **attributeName**: The name of the attribute as listed in the csv. Required. eg: "c_temp"
* **attributeLabel**: A descriptive label that can be used to display the name of an attribute. It is not constrained by system limitations on length or special characters. Optional. eg: "Temperature (Celsius)"
* **attributeDefinition**: Longer description of the attribute, including the required context for interpreting the attributeName. Required. eg: "The nearshore water temperature in the upper intertidal zone, measured in degrees celsius."
* **measurementScale**: One of: nominal, ordinal, dateTime, ratio, interval. Required.
    + *nominal*: unordered categories or text. eg: (Male, Female) or (Yukon River, Kuskokwim River)
    + *ordinal*: ordered categories. eg: Low, Medium, High
    + *dateTime*: date or time values from the Gregorian calendar. eg: 01-01-2001
    + *ratio*: measurement scale with a meaningful zero point in nature. Ratios are proportional to the measured variable. e.g.: 0 Kelvin represents a complete absence of heat. 200 Kelvin is half as hot as 400 Kelvin. 1.2 meters per second is twice as fast as 0.6 meters per second.
    + *interval*: values from a scale with equidistant points, where the zero point is arbitrary. This is usually reserved for degrees Celsius or Fahrenheit, or latitude and longitude coordinates, or any other human-constructed scale. e.g.: there is still heat at 0° Celsius; 12° Celsius is NOT half as hot as 24° Celsius
* **domain**: One of: textDomain, enumeratedDomain, numericDomain, dateTimeDomain. Required.
    + *textDomain*: text that is free-form, or matches a pattern
    + *enumeratedDomain*: text that belongs to a defined list of codes and definitions. eg: CASC = Cascade Lake, HEAR = Heart Lake
    + *dateTimeDomain*: dateTime attributes
    + *numericDomain*: attributes that are numbers (either ratio or interval)
* **formatString**: Required for dateTimeDomain, NA otherwise. Format string for dates, eg "MM/DD/YYYY".
* **definition**: Required for textDomain, NA otherwise. Definition for attributes that are a character string, matches attribute definition in most cases.
* **unit**: Required for numericDomain, NA otherwise. Unit string. If the unit is not a standard unit, a warning will appear when you create the attribute list, saying that it has been forced into a custom unit. Use caution here to make sure the unit really needs to be a custom unit. A list of standard units can be found here: https://knb.ecoinformatics.org/#external//emlparser/docs/eml-2.1.1/./eml-unitTypeDefinitions.html#StandardUnitDictionary
* **numberType**: Required for numericDomain, NA otherwise. Options are "real", "natural", "whole", "integer".
    + *real*: positive and negative fractions and non fractions (...-1,-0.25,0,0.25,1...)
    + *natural*: non-zero positive counting numbers (1,2,3...)
    + *whole*: positive counting numbers and zero (0,1,2,3...)
    + *integer*: positive and negative counting numbers and zero (...-2,-1,0,1,2...)
* **missingValueCode**: Code for missing values (eg: '-999', 'NA', 'NaN'). NA otherwise. Note that an NA missing value code should be a string, 'NA', and numbers should also be strings, '-999.'
* **missingValueCodeExplanation**: Explanation for missing values, NA if no missing value code exists.

You can create attributes by hand by typing them out in R following a workflow similar to that as below.

```{r, eval = FALSE}
attributes <- data.frame(
    
    attributeName = c('Date', 'Location', 'Region','Sample_No', 'Sample_vol', 'Salinity', 'Temperature', 'sampling_comments'),
    attributeDefinition = c('Date sample was taken on', 'Location code representing location where sample was taken','Region where sample was taken', 'Sample number', 'Sample volume', 'Salinity of sample in PSU', 'Temperature of sample', 'comments about sampling process'),
    measurementScale = c('dateTime', 'nominal','nominal', 'nominal', 'ratio', 'ratio', 'interval', 'nominal'),
    domain = c('dateTimeDomain', 'enumeratedDomain','enumeratedDomain', 'textDomain', 'numericDomain', 'numericDomain', 'numericDomain', 'textDomain'),
    formatString = c('MM-DD-YYYY', NA,NA,NA,NA,NA,NA,NA),
    definition = c(NA,NA,NA,'Sample number', NA, NA, NA, 'comments about sampling process'),
    unit = c(NA, NA, NA, NA,'milliliter', 'dimensionless', 'celsius', NA),
    numberType = c(NA, NA, NA,NA, 'real', 'real', 'real', NA),
    missingValueCode = c(NA, NA, NA,NA, NA, NA, NA, 'NA'),
    missingValueCodeExplanation = c(NA, NA, NA,NA, NA, NA, NA, 'no sampling comments'),
    
    stringsAsFactors = FALSE)
```

Howerver, typing this out in R can be a major pain. Luckily, there is a shiny app that you can use to build attribute information. You can use the app to build attributes from a data file loaded into R (recommended as the app will autofill some fields for you), or to edit an existing attribute table, or create attributes from scratch using the following commands (the commands will launch a shiny app in your web browser).

```{r, eval = FALSE}
# From data (recommended)
datamgmt::create_attributes_table(data = data)

# From an attribute table
datamgmt::create_attributes_table(attributes_table = attributes_table)

# From scratch
datamgmt::create_attributes_table()
```

Once you are done editing a table in the app, click the `Print` button to print text of a code that will build a data frame in R. Copy that code and assign it to a variable in your script (e.g. `attributes <- data.frame(...)`).

### Edit Custom Units

If you have units that are not in the standard EML unit list, you will need to build a custom unit list. To determine if your units are standard or not you can look through the standard units by using the following commands.

```{r, eval = FALSE}
standardUnits <- get_unitList()
View(standardUnits$units)
```

Additionally, `datamgmt::create_attributes_table` will tell you if each of your units are standard or not. If your unit is not standard, you should use the following code to help autogenerate a custom unit.

``` {r, eval = FALSE}
datamgmt::get_custom_units("your_unit")
```

Note, `datamgmt::create_attributes_table` calls `datamgmt::get_custom_units` for you! Custom units need to have the following columns.

* **id** 
* **unitType**
* **parentSI**
* **multiplierToSI**
* **abbreviation**
* **definition**

`datamgmt::get_custom_units` will autogenerate many of these fields for you (**but don't just assume the autogeneration will be perfect, always ensure the autogeneration correctly handles your unit**)

### Edit Factors

For attributes that are `enumeratedDomains`, a table is needed with three columns: `attributeName`, `code`, and `definition`.

* **attributeName** should be the same as the `attributeName` within the attribute table and repeated for all codes belonging to a common attribute. 
* **code** should contain all unquie values of the given `attributeName` that exist within the actual data.
* **definition** should contain a plain text definition that describes each code.

There is a tab in the `datamgmt::create_attributes_table` app that will help you build factors.

If you need to build factors by hand, you can use named character vectors and then convert them to a data frame as shown in the example below.
In this example, there are two enumerated domains in the attribute list - "Location" and "Region"

```{r, eval = FALSE}
Location <- c(CASC = 'Cascade Lake', CHIK = 'Chikumunik Lake', HEAR = 'Heart Lake', NISH = 'Nishlik Lake' )
Region <- c(W_MTN = 'West region, locations West of Eagle Mountain', E_MTN = 'East region, locations East of Eagle Mountain')
```

The definitions are then written into a dataframe using the names of the named character vectors, and their definitions.

```{r, eval = FALSE}
factors <- rbind(data.frame(attributeName = 'Location', code = names(Location), definition = unname(Location)),
                  data.frame(attributeName = 'Region', code = names(Region), definition = unname(Region)))
```

### Finalize attributeList

Once you have built your attributes, factors, and custom units, you can add them to eml objects. Attributes and factors are combined to form an `attributeList` using the following command.

```{r, eval = FALSE}
attributeList <- EML::set_attributes(attributes = attributes,
                                     factors = factors) 
```

This `attributeList` must then be [added to a `dataTable`](#edit-datatables). Custom units are added to `additionalMetadata` using the following command.

```{r, eval = FALSE}
unitlist <- set_unitList(custom_units)
eml@additionalMetadata <- c(as(unitlist, "additionalMetadata"))
```