## Edit otherEntities

### Remove otherEntities

To remove an `otherEntity` use the following command. This may be useful if a data object is originally listed as an `otherEntity` and then transferred to a `dataTable`.

```{r, eval = FALSE}
eml@dataset@otherEntity[[i]] <- NULL
```

### Create otherEntities

If you need to create/update an `otherEntity`make sure to [publish](#publish-an-object) or [update](#update-an-object) your data object first (if it is not already on the DataONE node). Then build your `otherEntity`.

```{r, eval = FALSE}
otherEntity <- arcticdatautils::pid_to_eml_other_entity(mn, pkg$data[[i]])[[1]]
```

Alternatively, you can build the `otherEntity` of a data object not in your package by simply inputting the data pid.

```{r, eval = FALSE}
otherEntity <- arcticdatautils::pid_to_eml_other_entity(mn, "your_data_pid")[[1]]
```

Next, give the `otherEntity` a name and description.

```{r, eval = FALSE}
otherEntity@entityName <- as("A descriptive name for the data", "entityName")
otherEntity@entityDescription <- as("A description of the data", "entityDescription")
```

The `otherEntity` must then be set to the eml i.e. 

``` {r, eval = FALSE}
eml@dataset@otherEntity[[i]] <- otherEntity
```

