## Edit otherEntities

### Remove otherEntities

To remove an `otherEntity` use the following command. This may be useful if a data object is originally listed as an `otherEntity` and then transferred to a `dataTable`.

```{r, eval = FALSE}
eml@dataset@otherEntity[[i]] <- NULL
```

### Create otherEntities

If you need to create/update an `otherEntity`, make sure to [publish](#publish-an-object) or [update](#update-a-data-file) your data object first (if it is not already on the DataONE MN). Then build your `otherEntity`.

```{r, eval = FALSE}
otherEntity <- arcticdatautils::pid_to_eml_entity(mn, pkg$data[[i]])[[1]]
```

Alternatively, you can build the `otherEntity` of a data object not in your package by simply inputting the data `PID`.

```{r, eval = FALSE}
otherEntity <- arcticdatautils::pid_to_eml_entity(mn, "your_data_pid", entityName = "Entity Name", entityDescription = "Description about entity")
```

The `otherEntity` must then be set to the EML, like so: 

``` {r, eval = FALSE}
eml@dataset@otherEntity <- otherEntity
```

If you have additional `otherEntity`'s in the EML already, you will need to add the new one like this:

```{r, eval = FALSE}
eml@dataset@otherEntity[[i]] <- otherEntity
```

Where `i` is set to the number of existing entities plus one.