### Edit custom units

EML has a set list of units that can be added to an EML file. These can be seen by using the following code:

```{r, eval = FALSE}
standardUnits <- EML::get_unitList()
View(standardUnits$units)
```

If you have units that are not in the standard EML unit list, you will need to build a custom unit list. A unit typically consists of the following fields:

* **id**: The `unit id` (ids are camelCased)
* **unitType**: The `unitType` (run `View(standardUnits$unitTypes)` to see standard `unitType`s)
* **parentSI**: The `parentSI` unit (e.g. for kilometer `parentSI` = "meter")
* **multiplierToSI**: Multiplier to the `parentSI` unit (e.g. for kilometer `multiplierToSI` = 1000)
* **name**: Unit abbreviation (e.g. for kilometer `name` = "km")
* **description**: Text defining the unit (e.g. for kilometer `description` = "1000 meters")

To manually generate the custom units list, create a dataframe with the fields mentioned above. An example is provided below that can be used as a template:

```{r, eval = FALSE}
custom_units <- data.frame(
    
  id = c('siemensPerMeter', 'decibar'),
  unitType = c('resistivity', 'pressure'),
  parentSI = c('ohmMeter', 'pascal'),
  multiplierToSI = c('1','10000'),
  abbreviation = c('S/m','decibar'),
  description = c('siemens per meter', 'decibar'),
  
  stringsAsFactors = FALSE)
```

Using `EML::get_unit_id` for custom units will also generate valid EML unit ids. 

Custom units are then added to `additionalMetadata` using the following command:

```{r, eval = FALSE}
unitlist <- set_unitList(custom_units, as_metadata = TRUE)
doc$additionalMetadata <-  list(metadata = list(unitList = unitlist))
```
