## Edit attributeLists

Attributes are stored in an <a href = 'https://eml.ecoinformatics.org/images/eml-attribute.png' target='_blank'>attributeList</a>. When editing attributes in R, you need to create one to three objects:

1. A data.frame of attributes
2. A data.frame of custom units (if applicable)

Attributes can exist in EML for `dataTable`, `otherEntity`, and `spatialVector` data objects. Please note that submitting attribute information through the website will store them in an `otherEntity` object by default. We prefer to store them in a `dataTable` object for tabular data or a `spatialVector` object for spatial data.

To edit or examine an existing attribute table already in an EML file, you can use the following commands, where `i` represents the index of the series element you are interested in. Note that if there is only one item in the series (ie there is only one `dataTable`), you should just call `doc$dataset$dataTable`, as in this case `doc$dataset$dataTable[[1]]` will return the first sub-element of the `dataTable` (the `entityName`)

```{r, eval = FALSE}
# If they are stored in an otherEntity (submitted from the website by default)
attributeList <- EML::get_attributes(doc$dataset$otherEntity[[i]]$attributeList)
# Or if they are stored in a dataTable (usually created by a datateam member)
attributeList <- EML::get_attributes(doc$dataset$dataTable[[i]]$attributeList)
# Or if they are stored in a spatialVector (usually created by a datateam member)
attributeList <- EML::get_attributes(doc$dataset$spatialVector[[i]]$attributeList)

attributes <- attributeList$attributes
print(attributes)
```

### Edit attributes

Attribute information should be stored in a `data.frame` with the following columns:

* **attributeName**: The name of the attribute as listed in the csv. Required. e.g.: "c_temp"
* **attributeLabel**: A descriptive label that can be used to display the name of an attribute. It is not constrained by system limitations on length or special characters. Optional. e.g.: "Temperature (Celsius)"
* **attributeDefinition**: Longer description of the attribute, including the required context for interpreting the `attributeName`. Required. e.g.: "The near shore water temperature in the upper inter-tidal zone, measured in degrees Celsius."
* **measurementScale**: One of: nominal, ordinal, dateTime, ratio, interval. Required.
    + *nominal*: unordered categories or text. e.g.: (Male, Female) or (Yukon River, Kuskokwim River)
    + *ordinal*: ordered categories. e.g.: Low, Medium, High
    + *dateTime*: date or time values from the Gregorian calendar. e.g.: 01-01-2001
    + *ratio*: measurement scale with a meaningful zero point in nature. Ratios are proportional to the measured variable. e.g.: 0 Kelvin represents a complete absence of heat. 200 Kelvin is half as hot as 400 Kelvin. 1.2 meters per second is twice as fast as 0.6 meters per second.
    + *interval*: values from a scale with equidistant points, where the zero point is arbitrary. This is usually reserved for degrees Celsius or Fahrenheit, or latitude and longitude coordinates, or any other human-constructed scale. e.g.: there is still heat at 0° Celsius; 12° Celsius is NOT half as hot as 24° Celsius.
* **domain**: One of: `textDomain`, `enumeratedDomain`, `numericDomain`, `dateTime`. Required.
    + *textDomain*: text that is free-form, or matches a pattern
    + *enumeratedDomain*: text that belongs to a defined list of codes and definitions. e.g.: CASC = Cascade Lake, HEAR = Heart Lake
    + *dateTimeDomain*: `dateTime` attributes
    + *numericDomain*: attributes that are numbers (either `ratio` or `interval`)
* **formatString**: Required for `dateTime`, NA otherwise. Format string for dates, e.g. "DD/MM/YYYY".
* **definition**: Required for `textDomain`, NA otherwise. Definition for attributes that are a character string, matches attribute definition in most cases.
* **unit**: Required for `numericDomain`, NA otherwise. Unit string. If the unit is not a standard unit, a warning will appear when you create the attribute list, saying that it has been forced into a custom unit. Use caution here to make sure the unit really needs to be a custom unit. A list of standard units can be found using: `standardUnits <- EML::get_unitList()` then running `View(standardUnits$units)`.
* **numberType**: Required for `numericDomain`, NA otherwise. Options are `real`, `natural`, `whole`, and `integer`.
    + *real*: positive and negative fractions and integers (...-1,-0.25,0,0.25,1...)
    + *natural*: non-zero positive integers (1,2,3...)
    + *whole*: positive integers and zero (0,1,2,3...)
    + *integer*: positive and negative integers and zero (...-2,-1,0,1,2...)
* **missingValueCode**: Code for missing values (e.g.: '-999', 'NA', 'NaN'). NA otherwise. Note that an NA missing value code should be a string, 'NA', and numbers should also be strings, '-999.'
* **missingValueCodeExplanation**: Explanation for missing values, NA if no missing value code exists.

You can create attributes manually by typing them out in R following a workflow similar to the one below:

```{r, eval = FALSE}
attributes <- data.frame(
    
    attributeName = c('Date', 'Location', 'Region','Sample_No', 'Sample_vol', 'Salinity', 'Temperature', 'sampling_comments'),
    attributeDefinition = c('Date sample was taken on', 'Location code representing location where sample was taken','Region where sample was taken', 'Sample number', 'Sample volume', 'Salinity of sample in PSU', 'Temperature of sample', 'comments about sampling process'),
    measurementScale = c('dateTime', 'nominal','nominal', 'nominal', 'ratio', 'ratio', 'interval', 'nominal'),
    domain = c('dateTimeDomain', 'enumeratedDomain','enumeratedDomain', 'textDomain', 'numericDomain', 'numericDomain', 'numericDomain', 'textDomain'),
    formatString = c('MM-DD-YYYY', NA,NA,NA,NA,NA,NA,NA),
    definition = c(NA,NA,NA,'Sample number', NA, NA, NA, 'comments about sampling process'),
    unit = c(NA, NA, NA, NA,'milliliter', 'dimensionless', 'celsius', NA),
    numberType = c(NA, NA, NA,NA, 'real', 'real', 'real', NA),
    missingValueCode = c(NA, NA, NA,NA, NA, NA, NA, 'NA'),
    missingValueCodeExplanation = c(NA, NA, NA,NA, NA, NA, NA, 'no sampling comments'),
    
    stringsAsFactors = FALSE)
```

However, typing this out in R can be a major pain. Luckily, there's a Shiny app that you can use to build attribute information. You can use the app to build attributes from a data file loaded into R (recommended as the app will auto-fill some fields for you) to edit an existing attribute table, or to create attributes from scratch. Use the following commands to create or modify attributes (these commands will launch a Shiny app in your web browser):

```{r, eval = FALSE}
#first download the CSV in your data package from Exercise #2
data <- read.csv(text=rawToChar(getObject(adc_test, pkg$data)))
```

```{r, eval = FALSE}
# From data (recommended)
EML::shiny_attributes(data = data)

# From an existing attribute table
attributeList <- get_attributes(doc$dataset$dataTable[[i]]$attributeList)
EML::shiny_attributes(data = NULL, attributes = attributeList$attributes)

# From scratch
atts <- EML::shiny_attributes()
```

Once you are done editing a table in the app, quit the app and the tables will be assigned to the `atts` variable as a list of data frames (one for attributes, factors, and units). Alternatively, each table can be to exported to a csv file by clicking the `Download` button.

If you downloaded the table, read the table back into your R session and assign it to a variable in your script (e.g. `attributes <- data.frame(...)`), or just use the variable that `shiny_attributes` returned.

For simple attribute corrections, `datamgmt::edit_attribute()` allows you to edit the slots of a single attribute within an attribute list. To use this function, pass an attribute through `datamgmt::edit_attribute()` and fill out the parameters you wish to edit/update. An example is provided below where we are changing `attributeName`, `domain`, and `measurementScale` in the first attribute of a dataset. After completing the edits, insert the new version of the attribute back into the EML document.

```{r, eval = FALSE}

new_attribute <- datamgmt::edit_attribute(doc$dataset$dataTable[[1]]$attributeList$attribute[[1]], attributeName = 'date_and_time', domain = 'dateTimeDomain', measurementScale = 'dateTime')
doc$dataset$dataTable[[1]]$attributeList$attribute[[1]] <- new_attribute

```
 
### Edit custom units

EML has a set list of units that can be added to an EML file. These can be seen by using the following code:

```{r, eval = FALSE}
standardUnits <- EML::get_unitList()
View(standardUnits$units)
```

Search the units list for your unit before attempting to create a custom unit. You can search part of the unit you can look up part of the unit ie `meters` in the table to see if there are any matches.

If you have units that are not in the standard EML unit list, you will need to build a custom unit list. A unit typically consists of the following fields:

* **id**: The `unit id` (ids are camelCased)
* **unitType**: The `unitType` (run `View(standardUnits$unitTypes)` to see standard `unitType`s)
* **parentSI**: The `parentSI` unit (e.g. for kilometer `parentSI` = "meter")
* **multiplierToSI**: Multiplier to the `parentSI` unit (e.g. for kilometer `multiplierToSI` = 1000)
* **name**: Unit abbreviation (e.g. for kilometer `name` = "km")
* **description**: Text defining the unit (e.g. for kilometer `description` = "1000 meters")

To manually generate the custom units list, create a dataframe with the fields mentioned above. An example is provided below that can be used as a template:

```{r, eval = FALSE}
custom_units <- data.frame(
    
  id = c('siemensPerMeter', 'decibar'),
  unitType = c('resistivity', 'pressure'),
  parentSI = c('ohmMeter', 'pascal'),
  multiplierToSI = c('1','10000'),
  abbreviation = c('S/m','decibar'),
  description = c('siemens per meter', 'decibar'),
  
  stringsAsFactors = FALSE)
```

Using `EML::get_unit_id` for custom units will also generate valid EML unit ids. 

Custom units are then added to `additionalMetadata` using the following command:

```{r, eval = FALSE}
unitlist <- set_unitList(custom_units, as_metadata = TRUE)
doc$additionalMetadata <-  list(metadata = list(unitList = unitlist))
```

### Edit factors

For attributes that are `enumeratedDomains`, a table is needed with three columns: `attributeName`, `code`, and `definition`.

* **attributeName** should be the same as the `attributeName` within the attribute table and repeated for all codes belonging to a common attribute. 
* **code** should contain all unique values of the given `attributeName` that exist within the actual data.
* **definition** should contain a plain text definition that describes each code.

To build factors by hand, you use the named character vectors and then convert them to a data.frame as shown in the example below. In this example, there are two enumerated domains in the attribute list - "Location" and "Region".

```{r, eval = FALSE}
Location <- c(CASC = 'Cascade Lake', CHIK = 'Chikumunik Lake', HEAR = 'Heart Lake', NISH = 'Nishlik Lake' )
Region <- c(W_MTN = 'West region, locations West of Eagle Mountain', E_MTN = 'East region, locations East of Eagle Mountain')
```

The definitions are then written into a data.frame using the names of the named character vectors and their definitions.

```{r, eval = FALSE}
factors <- rbind(data.frame(attributeName = 'Location', code = names(Location), definition = unname(Location)),
                  data.frame(attributeName = 'Region', code = names(Region), definition = unname(Region)))
```

### Finalize attributeList

Once you have built your attributes, factors, and custom units, you can add them to EML objects. Attributes and factors are combined to form an `attributeList` using the following command:

```{r, eval = FALSE}
attributeList <- EML::set_attributes(attributes = attributes,
                                     factors = factors) 
```

This `attributeList` must then be [added to a `dataTable`](#edit-datatables).
