## Edit dataTables

To edit a `dataTable`, first [edit/create an `attributeList`](#edit-attributelists) and [set the physical](#set-physical). 
Then create a new `dataTable` using the `eml$dataTable()` helper function as below:

```{r, eval = FALSE}
dataTable <- eml$dataTable(entityName = "A descriptive name for the data (does not need to be the same as the data file)",
                 entityDescription = "A description of the data",
                 physical = physical,
                 attributeList = attributeList)
```

The `dataTable` must then be added to the EML. How exactly you do this will depend on whether there are `dataTable` elements in your EML, and how many there are. To replace whatever dataTable elements already exist, you could write:

```{r, eval = FALSE}
doc$dataset$dataTable <- dataTable
```

If there is only one `dataTable` in your dataset, the EML package will usually "unpack" these, so that it is not contained within a list of length 1 - this means that to add a second `dataTable`, you cannot use the syntax `doc$dataset$dataTable[[2]]`, since when unpacked this will contain the `entityDescription` as opposed to pointing to the second in a series of `dataTable` elements. Confusing - I know. Not to fear though - this syntax will get you on your way, should you be trying to add a second `dataTable`.

```{r, eval = FALSE}
doc$dataset$dataTable <- list(doc$dataset$dataTable, dataTable)
```

If there is more than one `dataTable` in your dataset, you can return to the more straightforward construction of:

```{r, eval = FALSE}
doc$dataset$dataTable[[i]] <- dataTable 
```

Where `i` is the index that you wish insert your `dataTable` into.

To add a list of `dataTables` to avoid the unpacking problem above you will need to create a list of `dataTables`

```{r, eval = FALSE}
dts <- list() # create an empty list
for(i in seq_along(tables_you_need)){
  # your code modifying/creating the dataTable here
  dataTable <- eml$dataTable(entityName = dataTable$entityName,
                             entityDescription = dataTable$entityDescription,
                             physical = physical,
                             attributeList = attributeList)
  
  dts[[i]] <- dataTable # add to the list
}
```

After getting a list of `dataTables`, assign the resulting list to `dataTable` EML
```{r}
doc$dataset$dataTable <- dts
```

Sometimes the metadata intended for `dataTable` ends up in `otherEntity`. You can use `eml_otherEntity_to_dataTable` to easily move items in `otherEntity` over to `dataTable`. 
```{r, eval = FALSE}
eml_otherEntity_to_dataTable(doc, 
                             1, # which otherEntities you want to convert, for multiple use - 1:5
                             validate_eml = F) # set this to False if the physical or attributes are not added
```

