## Series Identifier (SID)
A series identifier is a system metadata field that represents a single identifier across multiple versions of a data package, a feature often requested by submitters.  These are useful for maintaining a single identifier when a data package is expected to receive updates (usually additional data) in the future. For example, this dataset has a series id:
https://doi.org/10.18739/A2154DQ22 (the doi and urn:uuid are both present at the top of the dataset).

### Adding a SID to a package
Adding a series identifier should be the last step.  In most cases the SID will be in `DOI` format.  Once the data package is complete (peer-reviewd and approved by the PI) the series identifier can be added by updating the `seriesId` field of the system metadata of the metadata object. 

```{r, eval=F}
# The metadata identifier we're assigning an SID to
metadata_pid <- 'metadata_pid'

sys <- getSystemMetadata(mn, metadata_pid)
sys@seriesId <- generateIdentifier(mn, scheme = 'DOI') #update the scheme argument if it should not be a DOI
updateSystemMetadata(mn, metadata_pid, sys)
```


### Updating the child packages of a parent package with a SID
When updating a parent package with a series identifier you need to use `update_resource_map` rather than `publish_update`.  In this case our goal is add nested data packages to an existing parent package. 

```{r, eval=F}
# Call get_package on the parent package that has a `seriesId` in its system metadata 
parent_package <- get_package(mn, 'resource_map_pid')
# The resource map of the package we want to add to the 'child_pids' of the parent
resource_map_new_child <- '' 

update_resource_map(mn, parent_package$resource_map, parent_package$metadata, parent_package$data,
                    c(parent_package$child_packages, resource_map_new_child))

```

### Updating the metadata of a package with a SID 
When updating the metadata (xml) of a package with a series identifier use `publish_update`.  It's important that you pass the metadata pid to the `metadata_pid` argument rather than `seriesId`.  The metadata pid will usually have the text "version: " ahead of it, however it's best to use `get_package` first to avoid mistakes. 
```{r, eval=F}
pkg <- get_package(mn, 'resource_map_pid')
pkg <- publish_update(mn, pkg$metadata, pkg$resource_map, pkg$data, 
                      child_pids = pkg$child_pids) # + any additional arguments to "publish_update"
```
