## Set methods

The methods tree in the EML section has many different options, visible in the [schema](https://knb.ecoinformatics.org/emlparser/docs/eml-2.1.1/eml-methods.png). You can create new elements in the methods tree by following the schema and using the `eml` helpers.

Another simple and potentially useful way to add methods to an EML that has no methods at all is by adding them via a MS Word document. An example is shown below:

```{r, eval = F}
methods1 <- set_methods('methods_doc.docx')
doc$dataset$methods <- methods1
```

If you want to make minor changes to existing methods information that has a lot of nested elements, your best bet may be to edit the EML manually in a text editor (or in RStudio), otherwise there is a risk of accidentally overwriting nested elements with blank object classes, therefore losing methods information.

### Adding sampling info to methods section

```{r, eval = FALSE}
# add method steps as new variables
step1 <- eml$methodStep(description = "text describing the methods used")

stEx <- eml$studyExtent(description = "study extent description")

samp <- eml$sampling(studyExtent = stEx,
                     samplingDescription = "sampling description text")


# combine all methods steps and sampling info 
methods1 <- eml$methods(methodStep = step1, 
                        sampling = samp)

doc$dataset$methods <- methods1
```
