## Set parties

To add people, with their addresses, you need to add addresses as their own object class, which you then add to the `contact`, `creator`, or `associatedParty` classes.

```{r, eval = FALSE}
NCEASadd <- eml$address( 
                deliveryPoint = "735 State St #300", 
                city = "Santa Barbara", 
                administrativeArea = 'CA', 
                postalCode = '93101')
```

The `creator`, `contact`, and `associatedParty` classes can easily be created using functions from the `arcticdatautils` package. Here, we use `eml_creator()` to set our data set `creator`.

```{r, eval = FALSE}
JC_creator <- arcticdatautils::eml_creator(given_names = "Jeanette", 
                                           sur_name = "Clark", 
                                           organization = "NCEAS", 
                                           email = "jclark@nceas.ucsb.edu", 
                                           phone = "123-456-7890", 
                                           userId = "https://orcid.org/WWWW-XXXX-YYYY-ZZZZ",
                                           address = NCEASadd)
doc$dataset$creator <- JC_creator
```

Similarly, we can set the `contact`s. In this case, there are two, so we set `eml@dataset@contact` as a `ListOfcontact`, which contains both of them.

```{r, eval = FALSE}
JC_contact <- arcticdatautils::eml_contact(given_names = "Jeanette", 
                                           sur_name = "Clark", 
                                           organization = "NCEAS", 
                                           email = "jclark@nceas.ucsb.edu", 
                                           phone = "123-456-7890",  
                                           userId = "https://orcid.org/WWWW-XXXX-YYYY-ZZZZ",
                                           address = NCEASadd)

JG_contact <- arcticdatautils::eml_contact(given_names = "Jesse", 
                                           sur_name = "Goldstein", 
                                           organization = "NCEAS", 
                                           email = "jgoldstein@nceas.ucsb.edu", 
                                           phone = "123-456-7890",  
                                           userId = "https://orcid.org/WWWW-XXXX-YYYY-ZZZZ",
                                           address = NCEASadd)

doc$dataset$contact <- list(JC_contact, JG_contact)
```

Finally, the `associatedParty`s are set. Note that `associatedParty`s MUST have a role defined, unlike `creator` or `contact`.

```{r, eval = FALSE}
JG_ap <- arcticdatautils::eml_associated_party(given_names = "Jesse", 
                                               sur_name = "Goldstein", 
                                               organization = "NCEAS", 
                                               email = "jgoldstein@nceas.ucsb.edu",
                                               phone = "123-456-7890",  
                                               address = NCEASadd, 
                                               userId = "https://orcid.org/WWWW-XXXX-YYYY-ZZZZ",
                                               role = "metaataProvider")
doc$dataset$associatedParty <- JG_ap
```
