## Set physical

To set the `physical` aspects of a data object, use the following commands to build a `physical` object from a data `PID` that exists in your package. **Remember to [set the member node](https://nceas.github.io/datateam-training/reference/set-dataone-nodes.html) to test.arcticdata.io !**

```{r, eval = FALSE}
physical <- arcticdatautils::pid_to_eml_physical(mn, pkg$data[[i]])
```

Alternatively, you can set the `physical` of a data object not yet in your package by simply inputting the data `PID`:

```{r, eval = FALSE}
physical <- arcticdatautils::pid_to_eml_physical(mn, "your_data_pid")
```

The `physical` must then be assigned to the data object.

A final, but not recommended option, is to set the `physical` by hand. To do so, one can use a workflow similar to the one below. However, the far superior workflow is to [publish](#publish-an-object) or [update](#update-a-data-file) your data first and then use `pid_to_eml_physical` to set the `physical`.

```{r, eval = FALSE}
id <- 'your_data_pid' # this should be an actual PID
path <- '~/your/data/path' # path to data table
physical <- EML::set_physical(objectName = 'your_file_name',
                              id = id,
                              size = as.character(file.size(path)),
                              sizeUnit = 'bytes',
                              authentication = digest(path, algo="sha1", serialize=FALSE, file=TRUE),
                              authMethod = 'SHA-1',
                              numHeaderLines = '1',
                              fieldDelimiter = ',',
                              url = paste0('https://cn.dataone.org/cn/v2/resolve/', id))
```