## Set methods

The methods tree in the EML section has many different options, visible in the [schema](https://knb.ecoinformatics.org/emlparser/docs/eml-2.1.1/eml-methods.png). You can create new elements in the methods tree by following the schema and using the `new` command. Remember you can explore possible slots within an element by creating an empty object of the class you are trying to create. For example, `method_step <- new('methodStep')`, and using auto-complete on `method_step@`.

Potentially the most useful way to set methods is by [editing with EML](#edit-eml-with-eml) 

Another simple and potentially useful way to add methods to an EML that has no methods at all is by adding them via a MS Word document. An example is shown below:

```{r, eval = F}
methods1 <- set_methods('methods_doc.docx')
eml@dataset@methods <- methods1
```

If you want to make minor changes to existing methods information that has a lot of nested elements, your best bet may be to edit the EML manually in a text editor (or in RStudio), otherwise there is a risk of accidentally overwriting nested elements with blank object classes, therefore losing methods information.

### Adding sampling info to methods section

```{r, eval = FALSE}
# add method steps as new variables
step1 <- new('methodStep',
             description = "methods text")

stEx <- new("studyExtent", 
           description = "study extent description")

samp <- new("sampling", 
           studyExtent = stEx,
           samplingDescription = "sampling description text")

# combine all methods steps and sampling info 
methods1 <- new("methods",
               methodStep = c(step1),
               sampling = samp)
               
eml@dataset@methods <- methods1
```
