## Set physical

To set the `physical` aspects of a data object, use the following commands to build a `physical` object from a data `PID` that exists in your package. **Remember to <a href = 'https://nceas.github.io/datateam-training/reference/set-dataone-nodes.html' target='_blank'>set the member node</a> to test.arcticdata.io!**

```{block, type = "note"}
The word ‘physical’ derives from database systems, which distinguish the ‘logical’ model (e.g., what attributes are in a table, etc) from the physical model (how the data are written to a physical hard disk (basically, the serialization). so,  we grouped metadata about the file (eg. dataformat, file size, file name) as written to disk in physical.
```

```{r, eval = FALSE}
physical <- arcticdatautils::pid_to_eml_physical(mn, pkg$data[[i]])
```

Alternatively, you can set the `physical` of a data object not yet in your package by simply inputting the data `PID`:

```{r, eval = FALSE}
physical <- arcticdatautils::pid_to_eml_physical(mn, "your_data_pid")
```

The `physical` must then be assigned to the data object.

Note that the above workflow only works if your data object already exists on the member node.


