## Set physical

To set the `physical` aspects of a data object, use the following commands to build a `physical` object from a data `PID` that exists in your package. **Remember to <a href = 'https://nceas.github.io/datateam-training/reference/set-dataone-nodes.html' target='_blank'>set the member node</a> to test.arcticdata.io!**

```{block, type = "note"}
The word ‘physical’ derives from database systems, which distinguish the ‘logical’ model (e.g., what attributes are in a table, etc) from the physical model (how the data are written to a physical hard disk (basically, the serialization). so,  we grouped metadata about the file (eg. dataformat, file size, file name) as written to disk in physical.
```

```{r, eval = FALSE}
physical <- arcticdatautils::pid_to_eml_physical(mn, pkg$data[[i]])
```

Alternatively, you can set the `physical` of a data object not yet in your package by simply inputting the data `PID`:

```{r, eval = FALSE}
physical <- arcticdatautils::pid_to_eml_physical(mn, "your_data_pid")
```

The `physical` must then be assigned to the data object.

A final, but not recommended option, is to set the `physical` by hand. To do so, one can use a workflow similar to the one below. However, the far superior workflow is to <a href = 'https://nceas.github.io/datateam-training/reference/publish-an-object.html#publish-an-object' target='_blank'>publish</a> or <a href = 'https://nceas.github.io/datateam-training/reference/update-a-package-with-a-new-data-object.html' target='_blank'>update</a> your data first and then use `pid_to_eml_physical()` to set the `physical`.

```{r, eval = FALSE}
id <- 'your_data_pid' # this should be an actual PID
path <- '~/your/data/path' # path to data table
physical <- set_physical(objectName = path,
                              size = as.character(file.size(path)),
                              sizeUnit = 'bytes',
                              authentication = digest(fpath, algo="sha256", serialize=FALSE, file=TRUE),
                              authMethod = 'SHA-256',
                              numHeaderLines = '1',
                              fieldDelimiter = ',',
                              url = paste0('https://cn.dataone.org/cn/v2/resolve/', id))
```
