## Set parties

The `address`, `creator`, `contact`, and `associatedParty` classes can easily be created using functions from the `EML` package. However it is often easier to just edit this through the webform.

To add people, with their addresses, you need to add addresses as their own object class, which you then add to the `contact`, `creator`, or `associatedParty` classes.

```{r, eval = FALSE}
NCEASadd <- eml$address( 
                deliveryPoint = "735 State St #300", 
                city = "Santa Barbara", 
                administrativeArea = 'CA', 
                postalCode = '93101')
```

Here, we use `eml_creator()` to set our data set `creator`.

```{r, eval = FALSE}
JC_creator <- eml$creator(individualName = list(givenName = "Jeanette", 
                                                surName = "Clark"), 
                          organization = "NCEAS", 
                          electronicMailAddress = "jclark@nceas.ucsb.edu", 
                          phone = "123-456-7890", 
                          userId = "https://orcid.org/WWWW-XXXX-YYYY-ZZZZ",
                          address = NCEASadd)
doc$dataset$creator <- JC_creator
```

Similarly, we can set a single `contact` or multiple. In this case, there are two, so we set `doc$dataset$contact` as a list containing both of them.

```{r, eval = FALSE}
JC_contact <- eml$contact(individualName = list(givenName = "Jeanette", 
                                                surName = "Clark"), 
                          organization = "NCEAS", 
                          electronicMailAddress = "jclark@nceas.ucsb.edu", 
                          phone = "123-456-7890",  
                          userId = "https://orcid.org/WWWW-XXXX-YYYY-ZZZZ",id = eml$userId(directory = eml$dir)
                          address = NCEASadd)

JG_contact <- eml$contact(individualName = list(givenName = "Jesse", 
                                                surName = "Goldstein"), 
                          organization = "NCEAS", 
                          electronicMailAddress = "jgoldstein@nceas.ucsb.edu", 
                          phone = "123-456-7890",  
                          userId = "https://orcid.org/WWWW-XXXX-YYYY-ZZZZ",
                          address = NCEASadd)

doc$dataset$contact <- list(JC_contact, JG_contact)
```

Finally, the `associatedParty`s are set. Note that `associatedParty`s MUST have a role defined, unlike `creator` or `contact`.

```{r, eval = FALSE}
JG_ap <- eml$associatedParty(individualName = list(givenName = "Jesse", 
                                                   surName = "Goldstein"),
                             organization = "NCEAS", 
                             email = "jgoldstein@nceas.ucsb.edu",
                             electronicMailAddress = "123-456-7890",  
                             address = NCEASadd, 
                             userId = "https://orcid.org/WWWW-XXXX-YYYY-ZZZZ",
                             role = "metadataProvider")
doc$dataset$associatedParty <- JG_ap
```
