## File paths

This section contains some basic tips about file paths.

### Remote files vs. local files

If you're working on the datateam server (<a href = 'https://datateam.nceas.ucsb.edu/rstudio/auth-sign-in' target='_blank'>RStudio</a> in an internet browser), you're usually working in the home directory under your username.  File paths generally follow this pattern: `/home/dmullen/folder/file`. **Note:** These files are not stored on your local machine, they are on a remote server.  You can access them through remote SFTP software like Cyberduck.  

If you're working with your local RStudio app then your file paths generally follow this pattern: `/Users/datateam/folder/file`. These files are stored on your local machine and you can access them with Finder. 

### File path shortcuts

Using `.` in a file path refers to your current working directory. You can print your working directory with the call: `getwd()`.  If we assume that my current working directory is `home/dmullen`, then the following two calls are equivalent:

```{r, eval=FALSE}
file.exists('/home/dmullen/myFile.R')
file.exists('./myFile.R')
```

Using `~` in a file path does not **always** refer to your current working directory.  This is a common misconception.  It is actually set to the global R USER path.  You can print this with the call: `Sys.getenv('USER')`.  Let's assume that I'm working on the `arcticdatautils` package which I open using a `.RProj` file.  This will update my current working directory to: `/home/dmullen/arcticdatautils`.  Now the following calls are equivalent:

```{r, eval=FALSE}
file.exists('/home/dmullen/arcticdatautils/myFile.R')
file.exists('~/arcticdatautils/myFile.R')
file.exists('./myFile.R')
```
